### 2014-11-28 latex-spie/article.tex
SPIE14 uygun format

%  article.tex (Version 1.00, released 1 October 2013)
%  LaTeX source file to demonstrate formatting for manuscripts 
%  to be submitted to SPIE journals
%  based on the class file spieman.cls, which requires 
%  the following standard packages:  times.sty, float.sty, 
%  ifthen.sty, cite.sty, color.sty, setspace.sty
%
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, for example, to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class 
%  file (spieman.cls) and may not be understood in other classes:
%  \affiliations{}, \sup{},\supit{}, \authorinfo{}, \keywords{},
%  \linkable and \video
%  The bibliography style file is called spiejour.bst 
%  This article.tex file needs the following image files:
%  mcr3b.eps
%  fig2.eps
%  satellite.eps

%%\documentclass[12pt]{spieman}  %>>> 12pt font mandatory; use this for US letter paper 
\documentclass[a4paper,10pt]{spieman}  %>>> use this instead for A4 paper
%%\documentclass[nocompress,12pt]{spieman}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%  The following command loads a graphics package to include images 
%  in the document. It may be necessary to specify a DVI driver option,
%  for example, [dvips], but that may be inappropriate for some LaTeX installations. 
\usepackage{amsmath}  %>>> for AMS math formatting, 
%  including bold Greek symbols
\usepackage[]{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[]{times}

\title{Sample manuscript showing style and formatting specifications for SPIE journal papers}

%>>>> The author is responsible for formatting the 
%  author list and their affiliations.  Use \\ to force linebreaks.
%  The correspondence between each author and his/her address
%  can be indicated with a superscript, 
%  which is easily obtained with \supscr{}.
%>>>> After the abstract, the author must include
%  a list of keywords and contact information for the corresponding author.

\author{First Author,\supscr{a} Second Author,\supscr{a} Third Author,\supscr{b} Fourth Author\supscr{a,b}}

\affiliation{\supscrsm{a}University Name, Faculty Group, Department, Street Address, City, Country, Postal Code\\
\supscrsm{b}Company Name, Street Address, City, Country, Postal Code}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table} 
\begin{document} 
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
This document shows the required format and appearance of a manuscript prepared for SPIE journals. It is prepared using LaTeX2e with the class file {\tt spieman.cls}. The abstract should consist of a single paragraph containing no more than 200 words. It should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting and indexing databases, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. A list of up to eight keywords should immediately follow, with the keywords separated by commas and ending with a period. The body of the manuscript should be double-spaced and fully justified.   
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}

%>>>> Include contact information for corresponding author
{\noindent \footnotesize{\bf Address all correspondence to}: First author, University Name, Faculty Group, Department, Street Address, City, Country, Postal Code; Tel: +1 555-555-5555; Fax: +1 555-555-5556; E-mail:  \linkable{myemail@university.edu} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{spacing}{1}   % use double spacing for rest of manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sect:intro}  % \label{} allows reference to this section
This document shows the required format and appearance of a manuscript prepared for SPIE journals. Formatting guidelines must be carefully followed. Authors are advised to print this sample manuscript and use it as a reference while preparing their own paper, to ensure all guidelines are met.

%%-----------------------------------------------------------
\subsection{Use of This Document}

This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.  The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it. Authors may use it as a template to create their own manuscript. While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.

%%-----------------------------------------------------------
\subsection{English}

Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example. In addition, good English usage is essential. Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced. Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{http://spie.org/EnglishEditing}. SPIE authors will receive a 10\% discount off their services. A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission. Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.

%%-----------------------------------------------------------
\subsection{Page Setup and Fonts}

All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm). Manuscripts must be formatted for US letter paper, on which the margins should be 1.0 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in\ on the left and right.

The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}. If this font is not available, use a similar serif font. The manuscript should not contain headers or footers. Pages should be numbered.

%% Use of [h] in following command forces table to appear "here", instead of a top or bottom of page, which is generally preferred.
\begin{table}[h]
\caption{Fonts sizes and styles.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
\hline\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
\hline 
\end{tabular}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parts of Manuscript}

This section describes the normal structure of a manuscript and how each part should be handled. The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.

%%-----------------------------------------------------------
\subsection{Title and Author Information} 
\label{sect:title}
The article title appears left justified at the top of the first page. The title font is 16 pt., bold. The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized. Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.). The word “novel” should not appear in the title, as publication will imply novelty. Avoid the use of acronyms in the title, unless they are widely understood. Appendix A contains more about acronyms.

The list of authors immediately follows the title, 18 points below. The font is 12 pt., bold and the author names are left justified. The author affiliations and addresses follow the names, in 10-pt., normal font and left justified. For multiple affiliations, each affiliation should appear on a separate line. Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations. Corresponding author should be listed below the Keywords, following the line ``Address all correspondence to:"; include mailing address, telephone, fax, and E-mail address.

%%-----------------------------------------------------------
\subsection{Abstract} 
The abstract should be a concise summary of the paper. Because the abstract may be used in abstracting journals, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. It should not exceed 200 words. For further guidelines, please read the brief article titled ``How to Write an Abstract (PDF)," \\(\linkable{http://spie.org/Documents/Publications/How to Write an Abstract.pdf}) by Philip Koopman. (Courtesy of Philip Koopman, Carnegie Mellon University.) Note the underlined link must be written on a single line in order for the link to function. Thus, a break in the line, created with {\verb+\\+} is required before the link or the preceding text should be editted to gracefully place the link on a single line. This type of adjustment is best done at end of the manuscript-preparation process.

%%-----------------------------------------------------------
\subsection{Keywords} 
Up to eight keywords should be specified.

%%-----------------------------------------------------------
\subsection{Body of Paper} 
The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.

To provide transition elements in your paper, it is important to refer back (or forward) to specific sections. Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed..." or ``Section 2.1 contained a description..." If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out. When occurring in the middle of a sentence, these words are abbreviated Sect., Ref., Eq., and Fig.

At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).

%%-----------------------------------------------------------
\subsection{Footnotes} 
Use textual footnotes only when necessary to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should be avoided. If absolutely necessary, the footnote mark must come at the end of a sentence. To insert a footnote, use the {\verb|\footnote{}|} command.

%%-----------------------------------------------------------
\subsection{Appendices} 
SPIE journals do not accept supplementary materials. However, it is acceptable to include an Appendix when necessary,  details such as derivations of equations, proofs of theorems, and details of algorithms. Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.

%%-----------------------------------------------------------
\subsection{Acknowledgments} 
In the acknowledgments section, which appears just before the references, the authors may credit others for their guidance or help. Also, funding sources or sponsorship information may be stated. The acknowledgments section does not have a section number.

%%-----------------------------------------------------------
\subsection{References} 
The References section lists books, articles, and reports that are cited in the paper. This section does not have a section number. The references are numbered in the order in which they are cited. Examples of the format to be followed are given at the end of this document.

The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.  The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.  Alternatively, the references may be directly formatted in the LaTeX source file.

For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.  Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.  A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.  References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.

The references are numbered in the order of their first citation. Citations to the references are made using superscripts, as demonstrated in the preceding paragraph. One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ..."  Two or more references should be separated by a comma with no space between them. Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.

%%---------------------------
\subsubsection{Reference linking and DOIs} 
A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet. The use of DOIs allows readers to easily access cited articles. Authors should include the DOI at the end of each reference in brackets, if a DOI is available. See examples at the end of this manuscript. A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}. The inclusion of DOIs will facilitate reference linking and is highly recommended.

In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note" in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}. The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.

%%-----------------------------------------------------------
\subsection{Biographies} 
A brief professional biography not to exceed 75 words may be provided for each author, if available. Biographies should be placed at the end of the paper, after the references. Personal information such as hobbies or birthplace/birthdate should not be included. Author photographs are not published.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Section Formatting} \label{sect:sections}

In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections. Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references. (Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.

Main section headings are in 12-pt., bold font, left-justified and in title case, where important words are capitalized.

Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style. The same goes for leading paragraphs of subsections and sub-subsections. Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation. There is no additional space between paragraphs. In LaTeX, paragraphs are separated by blank lines in the source file. Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.

%%-----------------------------------------------------------
\subsection{Subsection Headings} 
All important words in a subsection (level 1) header are capitalized. Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end. The heading is left justified and its font is 12 pt., italic.

%%-----------
\subsubsection{Sub-subsection headings} 
The first word of a sub-subsection is capitalized. The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known). The heading is left justified and its font is 11 pt., italic.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Figures and Tables}

%%-----------------------------------------------------------
\subsection{Figures}

Figures are numbered in the order in which they are called out in the text. They should appear in the document in numerical order and as close as possible to their first reference in the text. It may be necessary to move figures or tables around to enhance readability. LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.

Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered. Figure captions are centered below the figure or graph. Figure captions start with the abbreviation ``Fig" in front of the figure number, followed by a period, and the text in 10-pt. font. See Fig.~\ref{fig:example} for an example.

%%  Use following command to specify that graphics file is in 
%%  a directory other than this LaTeX source file.
%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=5.5cm]{mcr3b.eps}
   \end{tabular}
   \end{center}
   \caption 
   { \label{fig:example} %>> use \label inside caption to get Fig. number with \ref{}
Example of a figure caption. } 
   \end{figure} 
%-------------
Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.  In no case, should the article's text be wrapped around a figure. Figure~\ref{fig:example2} shows two side-by-side images. When a figure contains more than one image, the author must submit them as a single image file. Further details about figure formatting can be found at \linkable{http://spie.org/x85020.xml
\#Components}.

%------------- 
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
     \\
     (a) \hspace{5.1cm} (b)
   \end{tabular}
   \end{center}
   \caption 
   { \label{fig:example2} %>> use \label inside caption to get Fig. number with \ref{}
Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
   \end{figure}

%-------------%%-----------------------------------------------------------
\subsection{Tables} 
Tables are numbered in the order in which they are referenced. They should appear in the document in numerical order and as close as possible to their first reference in the text. It is preferable to have tables appear at the top or bottom of the page, if possible. Table captions are handled identically to those for figures, except that they appear above the table. See Table~\ref{tab:fonts} for an example.
%%-----------------------------------------------------------

\subsection{Multimedia} 
Please refer to the multimedia guidelines at \linkable{http://spie.org/x85020.xml\#Multimedia} for specific submission guidelines and requirements. The following types of multimedia files are accepted: QuickTime Non-Streaming video (.qt or .mov), MPEG (.mpg or .mp4). The recommended maximum size for each multimedia file is 10-12 MB. Authors must insert a representative “still” image from the video file in the manuscript as a “figure.” This still image will be linked by the publisher to the actual video file, as will the caption label. Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures. Otherwise  The multimedia file type should be included in parentheses at the end of the figure caption, along with the file size. See Video \ref{vid:satellite} for an example.

%-------------
   \begin{video}
   \begin{center}
   {\includegraphics[height=5cm]{satellite.eps}}
   \\
   \end{center}
   \caption{\label{vid:satellite} Example of a multimedia still image (MPEG, 2.5 MB).}
   \end{video} 
%-------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix    %>>>> this command starts appendixes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Miscellaneous Formatting Details} \label{sect:misc}

At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.

%%-----------------------------------------------
\subsection{Formatting Equations} 
Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.  Important equations appear on their own line.  Such equations are centered.  For example, ``The expression for the field of view is
	\begin{equation}
	\label{eq:fov}
2 a = \frac{(b + 1)}{3c} \, ,
	\end{equation}
where $a$ is the ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.

Equations are considered to be part of a sentence and should be punctuated accordingly. In the above example, a comma appears after the equation because the next line is a subordinate clause. If the equation ends the sentence, a period should follow the equation. The line following an equation should not be indented unless it is meant to start a new paragraph. Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.

References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..." Note that the word ``Equation" is spelled out if it begins a sentence, but is abbreviated as ``Eq." otherwise. Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq." and the following equation number..

%%-----------------------------------------------------------
\subsection{Formatting Theorems}

To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.  The text of the theorem continues on the same line in normal, 10-pt. font, achieved in LaTeX using \verb|\footnotesize|.  For example,

\vspace{2ex}\noindent{\footnotesize{\bf Theorem 1.} For any unbiased estimator...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Some LaTeX Guidance} \label{sect:latex}

To work properly, the LaTeX style file {\ttfamily spieman.cls} used to create this document requires following LaTeX packages:
{\ttfamily times.sty}, {\ttfamily float.sty}, {\ttfamily ifthen.sty}, {\ttfamily setspace.sty}, \\{\ttfamily cite.sty} (version 4.01 or later), and {\ttfamily color.sty}. If you do not have them in your LaTeX environment, see your system manager, or download them from \linkable{http://www.ctan.org}.

The author is required to make sure his or her manuscript is properly formatted. LaTeX sometimes needs some help to avoid making gross formatting blunders. The source file for this document provides examples of how to cope with some of LaTeX's shortcomings.

%%-----------------------------------------------------------
\subsection{Margins and PostScript Fonts}

Manuscripts submitted for SPIE journals as Portable Document Format (PDF) files must be formatted for US-letter-size paper and have the correct margins. The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.

One may directly create a PDF file from the DVI file with the LaTeX utility {\ttfamily dvipdfm}, for example. No options are necessary. Appealing aspects of this utility are that Acrobat Distiller is not needed, and Type 1 PostScript fonts are automatically included in the resulting PDF file.  Furthermore, {\ttfamily dvipdfm} allows one to directly incorporate images in JPEG, PNG, and PDF formats, and not just EPS, which is normally used with LaTeX.

Alternatively, with an application such as Adobe Acrobat, PDF files can be created from PostScript (PS) files, which can be produced by DVIPS. In most cases, the following DVIPS options should be invoked.

An important DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file. This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.  The option ``{\ttfamily -P pdf}" makes DVIPS include these fonts in its output PS file.

LaTeX margins are related to the document's paper size. The paper size is set at two separate places in the process of creating a PS file. The first place is in {\ttfamily latex}. 
The second place is in the application DVIPS. DVIPS has its own default paper size, which can be overridden with the option ``{\ttfamily -t letter}" or ``{\ttfamily -t a4}".  
If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command.

The {\ttfamily times.sty} package produces a bug in the handling certain combinations of letters; for example, `fi' is interpretted as a British pound symbol. Use the option ``{\ttfamily -G0}" ( capital G and zero) to avoid this problem.

To summarize, the following DVIPS options are recommended when making the PS file: ``{\ttfamily -t letter -P pdf -G0}".

%%-----------------------------------------------------------
\subsection{Bold Math Symbols}

The math package from the American Mathematical Society allows one to easily produce bold math symbols, well beyond what is available in LaTeX. It also provides many useful capabilities for creating elaborate mathematical expressions. You need to load the AMS math package near the top of the LaTeX source file, right after the \verb+\documentclass+ command:\\[1ex]
\verb+\usepackage[]{amsmath}+ \\[1ex]
Then for bold math symbols, use \verb+\boldsymbol+; for example, 
\verb+$\boldsymbol{\pi}$+ 
yields a bold pi.  You can make it easier to use by defining a shorthand command:\\[1ex]
\verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
and then using it like so \verb+$\bm{\pi}$+.

Not all math symbols are available in bold.  In a pinch, you can use \verb+\pmb+ ("poor man's bold"), which is defined in \verb+amsmath+. This command approximates a bold character with a superposition of several, slightly displaced unbold characters.

If you want a Greek symbol in the article title, it should be both larger and bold. The easiest thing is to load the AMS math package as described above. 
Then, in the title, use something like:\\[1ex]
\verb+\title{Estimation of {$\boldsymbol\alpha$} by a Monte Carlo + \linebreak\verb+technique}+ \\[1ex]
Note that the command to create the alpha character is enclosed within braces to form a self-contained environment.

%%-----------------------------------------------------------
\subsection{Uppercase Letters and Special Symbols in BibTex and LaTeX}

BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case. LaTeX does the same thing for the article title. BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.

The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged within braces \verb!{}!. Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
\verb+ @article{Kaczmarz37,+ \\ 
\verb+ author = "S. Kaczmarz",+ \\ 
\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen + \linebreak\verb+linearer {G}leichungen",+ \\ 
\verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
\verb+ volume = "A35",+ \\ 
\verb+ pages  = "355-357",+ \\	
\verb+ year   = "1937"	} + \\[1ex]
This example shows the treatment for both umlauts and uppercase letters.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments 
This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%

\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiejour}   %>>>> makes bibtex use spiejour.bst

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Biographies of authors %%%%%

\vspace{2ex}\noindent{\bf First Author} is an assistant professor at the University of Optical Engineering. He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.  He is the author of more than 50 journal papers and has written three book chapters. His current research interests include optical interconnects, holography, and optoelectronic systems. He is a member of SPIE.

\vspace{1ex}
\noindent Biographies and photographs of the other authors are not available.

\listoffigures
\listoftables

\end{spacing}
\end{document}

### 2014-11-29 latex-spie/article.tex
test
spieman.cls is changed with spie.cls in article.tex file
Images moved to figures folder
Images are added.

@@
-%  article.tex (Version 1.00, released 1 October 2013)
-%  LaTeX source file to demonstrate formatting for manuscripts 
-%  to be submitted to SPIE journals
-%  based on the class file spieman.cls, which requires 
-%  the following standard packages:  times.sty, float.sty, 
-%  ifthen.sty, cite.sty, color.sty, setspace.sty
-%
-%  Special instructions are included in this file after the
-%  symbol %>>>>
-%  Numerous commands are commented out, but included to show how
-%  to effect various options, for example, to print page numbers, etc.
-%  This LaTeX source file is composed for LaTeX2e.
+%  article.tex (Version 3.3, released 19 January 2008)
+%  Article to demonstrate format for SPIE Proceedings
 
 %  The following commands have been added in the SPIE class 
-%  file (spieman.cls) and may not be understood in other classes:
-%  \affiliations{}, \sup{},\supit{}, \authorinfo{}, \keywords{},
-%  \linkable and \video
-%  The bibliography style file is called spiejour.bst 
-%  This article.tex file needs the following image files:
-%  mcr3b.eps
-%  fig2.eps
-%  satellite.eps
+%  file (spie.cls) and will not be understood in other classes:
+%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
+%  The bibliography style file is called spiebib.bst, 
+%  which replaces the standard style unstr.bst.
 
-%%\documentclass[12pt]{spieman}  %>>> 12pt font mandatory; use this for US letter paper 
-\documentclass[a4paper,10pt]{spieman}  %>>> use this instead for A4 paper
-%%\documentclass[nocompress,12pt]{spieman}  %>>> to avoid compression of citations
+%----------------------------------------------------------------------------------------------------
+% PACKAGES
+%----------------------------------------------------------------------------------------------------
+
+\documentclass[]{spie}  % use for US letter paper
+\usepackage{comment}
+%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
+%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
 %% \addtolength{\voffset}{9mm}   %>>> moves text field down
-%  The following command loads a graphics package to include images 
-%  in the document. It may be necessary to specify a DVI driver option,
-%  for example, [dvips], but that may be inappropriate for some LaTeX installations. 
-\usepackage{amsmath}  %>>> for AMS math formatting, 
-%  including bold Greek symbols
+%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
 \usepackage[]{graphicx}
-\usepackage{setspace}
-\usepackage{tocloft}
-\usepackage[]{times}
+\usepackage{epsfig}		% TeX will automatically convert eps --> pdf in pdflatex	
+\usepackage{epstopdf}
+\usepackage{caption}
+\usepackage{subcaption}
 
-\title{Sample manuscript showing style and formatting specifications for SPIE journal papers}
+%----------------------------------------------------------------------------------------------------
+% TITLE
+%----------------------------------------------------------------------------------------------------
 
-%>>>> The author is responsible for formatting the 
-%  author list and their affiliations.  Use \\ to force linebreaks.
-%  The correspondence between each author and his/her address
-%  can be indicated with a superscript, 
-%  which is easily obtained with \supscr{}.
-%>>>> After the abstract, the author must include
-%  a list of keywords and contact information for the corresponding author.
+\title{An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation}
 
-\author{First Author,\supscr{a} Second Author,\supscr{a} Third Author,\supscr{b} Fourth Author\supscr{a,b}}
+%----------------------------------------------------------------------------------------------------
+% AUTHORS
+%----------------------------------------------------------------------------------------------------
 
-\affiliation{\supscrsm{a}University Name, Faculty Group, Department, Street Address, City, Country, Postal Code\\
-\supscrsm{b}Company Name, Street Address, City, Country, Postal Code}
+\author{
+Can Erhan\supit{a}, 
+Evangelos Sariyanidi\supit{b}, 
+Onur Sencan\supit{c}, 
+Hakan Temeltas\supit{c}
+\skiplinehalf
+\supit{a}Istanbul Technical University Mechatronics Engineering Department, Maslak 34469, Istanbul, Turkey; 
+\supit{b}Queen Mary University of London School of Electronic Engineering and Computer Science, ADDRESS, London, England; 
+\supit{c}Istanbul Technical University Control and Automation Engineering Department, Maslak 34469, Istanbul, Turkey
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\renewcommand{\cftdotsep}{\cftnodots}
-\cftpagenumbersoff{figure}
-\cftpagenumbersoff{table} 
+\authorinfo{Further author information: \\
+Can Erhan: E-mail: erhanc@itu.edu.tr \\  
+Evangelos Sariyanidi: E-mail: e.sariyanidi@eecs.qmul.ac.uk \\
+Onur Sencan: E-mail: osencan@itu.edu.tr \\  
+Hakan Temeltas: E-mail: hakan.temeltas@itu.edu.tr}
+% when using amstex, you need to use @@ instead of @
+
+% uncomment following for page numbers
+% \pagestyle{plain}    
+% uncomment following to start page numbering at 301 
+% \setcounter{page}{301}
+
+ %----------------------------------------------------------------------------------------------------
+% ABSTRACT
+%----------------------------------------------------------------------------------------------------
+
  \begin{document} 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 \begin{abstract}
-This document shows the required format and appearance of a manuscript prepared for SPIE journals.
-It is prepared using LaTeX2e with the class file {\tt spieman.cls}.
-The abstract should consist of a single paragraph containing no more than 200 words.
-It should be a summary of the paper and not an introduction.
-Because the abstract may be used in abstracting and indexing databases, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-A list of up to eight keywords should immediately follow, with the keywords separated by commas and ending with a period.
-The body of the manuscript should be double-spaced and fully justified.
+Visual loop closure detection problem is an active area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
+In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction with saliency detection technique.
+In contradistinction to the previous methods, our approach uses additional depth information.
+Saliency regions are used to refer to the certain distinctive areas on the image patches.
+They are also suitable to represent locations in a sparse manner.
+In order to find out the similarity between two locations we use a straightforward function, that contains the detection confidences of the image and the landmark coordinates in 3D.
+Recognition of the previously visited and unvisited locations is also considered in the framework.
+Exemplary results and the practical implementation of the method are also given with the data gathered on the testbed with a depth camera (Kinect) mounted differential drive autonomous ground vehicle.
+Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location.
 \end{abstract}
 
-%>>>> Include a list of up to six keywords after the abstract
-\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}
+\keywords{Loop closure, depth map, zernike moments,  computer vision}
 
-%>>>> Include contact information for corresponding author
-{\noindent \footnotesize{\bf Address all correspondence to}: First author, University Name, Faculty Group, Department, Street Address, City, Country, Postal Code; Tel: +1 555-555-5555; Fax: +1 555-555-5556; E-mail:  \linkable{myemail@university.edu} }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%----------------------------------------------------------------------------------------------------
+% INTRODUCTION
+%----------------------------------------------------------------------------------------------------
 
-\begin{spacing}{1}   % use double spacing for rest of manuscript
+\section{INTRODUCTION}
+\label{sec:intro}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sect:intro}  % \label{} allows reference to this section
-This document shows the required format and appearance of a manuscript prepared for SPIE journals.
-Formatting guidelines must be carefully followed.
-Authors are advised to print this sample manuscript and use it as a reference while preparing their own paper, to ensure all guidelines are met.
+In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
+One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM) which still remains as an assertive problem in a lot of ways.
+Loop closing is defined as the correct identification of previously visited location in terms of SLAM.
+Information that is gathered from various data sources including LIDARs, RADARs, stereo       and monocular cameras is highly utilized in loop closure detection.
+With the recent development of visual sensor technologies, the loop closure detection becomes a problem that is open for research in the field of computer vision.
 
-%%-----------------------------------------------------------
-\subsection{Use of This Document}
+In this paper, we present an enhanced loop closure method based on image-to-image matching in indoor environments with the additional depth information.
+Specifically, we adopt visual place recognition without using any metrical information such as rotation and exact location to correctly identify the previously visited location.
+This technique is quite simple to provide low computational complexity and performs in real-time with high loop closing accuracy.
 
-This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.
-The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it.
-Authors may use it as a template to create their own manuscript.
-While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.
+The technique we implement relies on discrete Complex Zernike Moments (CZMs) in 2-dimensional space.
+They are extracted using a set of complex polynomials which form a complete orthogonal radial basis functions defined on the unit disc.
+These moments are used to represent shape information inside the image within the context of image processing.
+In this study, the use of CZMs are examined in predefined non-overlapping patches of the image.
+The complex moments
 
-%%-----------------------------------------------------------
-\subsection{English}
+%----------------------------------------------------------------------------------------------------
+% METHODOLOGY
+%----------------------------------------------------------------------------------------------------
 
-Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
-In addition, good English usage is essential.
-Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced.
-Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{http://spie.org/EnglishEditing}.
-SPIE authors will receive a 10\% discount off their services.
-A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission.
-Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.
+\section{METHODOLOGY}
+\label{sec:method}
 
-%%-----------------------------------------------------------
-\subsection{Page Setup and Fonts}
+Methodology will be written here.
 
-All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm).
-Manuscripts must be formatted for US letter paper, on which the margins should be 1.0 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in\ on the left and right.
+%----------------------------------------------------------------------------------------------------
+% EXPERIMENTS
+%----------------------------------------------------------------------------------------------------
 
-The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}.
+\section{EXPERIMENTS}
+\label{sec:exper}
+
+Experiments will be written here.
+
+Location offset: 100 frames
+
+% DISTANCE MATRICES
+\begin{figure}[!htb]
+        \centering
+
+        %%% BRIGHT DISTANCE MATRIX
+        \begin{subfigure}[b]{0.27\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dist_bright.png}    
+        \caption{Bright distances}
+        \label{subfig:dist_bright}
+        \end{subfigure}
+        ~ 
+        %%% DIM DISTANCE MATRIX
+        \begin{subfigure}[b]{0.27\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dist_dim.png}    
+        \caption{Dim distances}
+        \label{subfig:dist_dim}
+        \end{subfigure}
+         ~ 
+        %%% DARK DISTANCE MATRIX
+        \begin{subfigure}[b]{0.27\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dist_dark.png}    
+        \caption{Dark distances}
+        \label{subfig:dist_dark}
+        \end{subfigure}
+
+        \hspace{-3mm}
+        \caption{Distance matrixes}
+        \label{fig:dist_matrices}
+\end{figure}
+
+%%% DATASET EXAMPLES
+\begin{figure}[!htb]
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=7cm]{figures/dataset_examples.png}
+        \caption{Dataset examples: (right) bright, (middle) dim, (left) dark}
+        \label{fig:dataset}
+\end{figure}
+
+%%% BRIGHT PR CURVE
+\begin{figure}[!htb]
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_bright.eps}    
+        \caption{Bright dataset results}
+        \label{fig:pr_bright}
+\end{figure}
+
+%%% DIM PR CURVE
+\begin{figure}[!htb]
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_dim.eps}    
+        \caption{Dim dataset results}
+        \label{fig:pr_dim}
+\end{figure}
+
+%%% DARK PR CURVE
+\begin{figure}[!htb]
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_dark.eps}      
+        \caption{Dark dataset results}
+        \label{fig:pr_dark}
+\end{figure}
+
+%----------------------------------------------------------------------------------------------------
+% ACKNOWLEDGEMENTS
+%----------------------------------------------------------------------------------------------------
+
+\acknowledgments
+
+Acknowledgements will be written here.
+
+%----------------------------------------------------------------------------------------------------
+% REFERENCES
+%----------------------------------------------------------------------------------------------------
+
+\bibliography{report}   %>>>> bibliography data in report.bib
+\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst
+
+\end{document}
+
+%----------------------------------------------------------------------------------------------------
+% % % % % % % % % % % % % % % % % % % % % % % % COMMENTED 
+%----------------------------------------------------------------------------------------------------
+
+\begin{comment}
+
+This document shows the desired format and appearance of a manuscript prepared for the Proceedings of the SPIE.\footnote{The basic format was developed in 1995 by Rick Herman (SPIE) and Ken Hanson (Los Alamos National Lab.).} It is prepared using LaTeX2e\cite{Lamport94} with the class file {\tt spie.cls}.
+The LaTeX source file used to create this document is {\tt article.tex}, which contains important formatting information embedded in it.
+These files are available on the Internet at {\tt http://home.lanl.gov/kmh/spie/}.
+The font used throughout is the LaTeX default font, Computer Modern Roman, which is equivalent to the Times Roman font available on many systems.
 If this font is not available, use a similar serif font.
-The manuscript should not contain headers or footers.
-Pages should be numbered.
+Normal text has a font size of 10 points\footnote{Font sizes are specified in points, abbreviated pt., which is a unit of length.
+One inch = 72.27 pt.; one cm = 28.4 pt.} for which the actual height of a capital E is about 2.4 mm (7 pt.) and the line-to-line spacing is about 4.2 mm (12 pt.).
+The font attributes for other parts of the manuscript, summarized in Table~\ref{tab:fonts}, are described in the following sections.
+Normal text should be justified to both the left and right margins.
+Appendix~\ref{sec:latex} has information about PostScript fonts.
 
-%% Use of [h] in following command forces table to appear "here", instead of a top or bottom of page, which is generally preferred.
+To be properly reproduced in the Proceedings, all text and figures must fit inside a rectangle 6.75-in.\ wide by 8.75-in.\ high or 17.15 cm by 22.23 cm.
+The text width and height are set in {\tt spie.cls} to match this requirement.
+%% This table is carefully placed in the source file to make 
+%% it appear at bottom of page, but above the footnotes.  
+%% Use of [h] in following command forces table to appear "here".
 \begin{table}[h]
-\caption{Fonts sizes and styles.} 
+\caption{Fonts sizes to be used for various parts of the manuscript.
+All fonts are Computer Modern Roman or an equivalent.
+Table captions should be centered above the table.
+When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.}
 \label{tab:fonts}
@@
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
-\hline\hline
-\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
+\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, centered  \\
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
+\rule[-1ex]{0pt}{3.5ex}  Author names and affiliations & 12 pt., normal, centered   \\
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
+\rule[-1ex]{0pt}{3.5ex}  Section heading & 11 pt., bold, centered (all caps)  \\
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
+\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 11 pt., bold, left justified  \\
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
+\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 10 pt., bold, left justified  \\
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
+\rule[-1ex]{0pt}{3.5ex}  Normal text & 10 pt., normal  \\
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
+\rule[-1ex]{0pt}{3.5ex}  Figure and table captions & \, 9 pt., normal \\
 \hline
-\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
+\rule[-1ex]{0pt}{3.5ex}  Footnote & \, 9 pt., normal \\
 \hline 
@@
 \end{table} 
+The text should begin 1.00 in.\ or 2.54 cm from the top of the page.
+The right and left margins should be 0.875~in.\ or 2.22 cm for US letter-size paper (8.5 in.\ by 11 in.) or 1.925 cm for A4 paper (210 mm by 297 mm) to horizontally center the text on the page.
+See Appendix~\ref{sec:latex} for guidance regarding paper-size specification.
+
+Authors are encouraged to follow the principles of sound technical writing, as described in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
+Many aspects of technical writing are addressed in the {\em AIP Style Manual}, published by the American Institute of Physics.
+It is available on line at {\tt http://www.aip.org/pubservs/style/4thed/toc.html} or {\tt http://public.lanl.gov/kmh/AIP\verb+_+Style\verb+_+4thed.pdf}.
+A spelling checker is helpful for finding misspelled words.
+
+An author may use this LaTeX source file as a template by substituting his/her own text in each field.
+This document is not meant to be a complete guide on how to use LaTeX.
+For that, refer to books on LaTeX usage, such as the definitive work by Lamport\cite{Lamport94} or the very useful compendium by Mittelbach et al.\cite{Mittelbach04}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parts of Manuscript}
+\section{PARTS OF MANUSCRIPT}
 
@@
 The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.
+In LaTeX, paragraphs are separated by blank lines in the source file.
 
-%%-----------------------------------------------------------
-\subsection{Title and Author Information} 
-\label{sect:title}
-The article title appears left justified at the top of the first page.
-The title font is 16 pt., bold.
-The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.
-Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.).
-The word “novel” should not appear in the title, as publication will imply novelty.
-Avoid the use of acronyms in the title, unless they are widely understood.
-Appendix A contains more about acronyms.
+At times it may be desired, for formatting reasons, to break a line without starting a new paragraph.
+This situation may occur, for example, when formatting the article title, author information, or section headings.
+Line breaks are inserted in LaTeX by entering \verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired location.
 
-The list of authors immediately follows the title, 18 points below.
-The font is 12 pt., bold and the author names are left justified.
-The author affiliations and addresses follow the names, in 10-pt., normal font and left justified.
-For multiple affiliations, each affiliation should appear on a separate line.
-Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations.
-Corresponding author should be listed below the Keywords, following the line ``Address all correspondence to:"; include mailing address, telephone, fax, and E-mail address.
-
-%%-----------------------------------------------------------
-\subsection{Abstract} 
-The abstract should be a concise summary of the paper.
-Because the abstract may be used in abstracting journals, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-It should not exceed 200 words.
-For further guidelines, please read the brief article titled ``How to Write an Abstract (PDF)," \\(\linkable{http://spie.org/Documents/Publications/How to Write an Abstract.pdf}) by Philip Koopman.
-(Courtesy of Philip Koopman, Carnegie Mellon University.) Note the underlined link must be written on a single line in order for the link to function.
-Thus, a break in the line, created with {\verb+\\+} is required before the link or the preceding text should be editted to gracefully place the link on a single line.
-This type of adjustment is best done at end of the manuscript-preparation process.
-
-%%-----------------------------------------------------------
-\subsection{Keywords} 
-Up to eight keywords should be specified.
-
-%%-----------------------------------------------------------
-\subsection{Body of Paper} 
-The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.
-
-To provide transition elements in your paper, it is important to refer back (or forward) to specific sections.
-Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed..." or ``Section 2.1 contained a description..." If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out.
-When occurring in the middle of a sentence, these words are abbreviated Sect., Ref., Eq., and Fig.
-
-At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).
-
-%%-----------------------------------------------------------
-\subsection{Footnotes} 
-Use textual footnotes only when necessary to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should be avoided.
-If absolutely necessary, the footnote mark must come at the end of a sentence.
-To insert a footnote, use the {\verb|\footnote{}|} command.
-
-%%-----------------------------------------------------------
-\subsection{Appendices} 
-SPIE journals do not accept supplementary materials.
-However, it is acceptable to include an Appendix when necessary,  details such as derivations of equations, proofs of theorems, and details of algorithms.
-Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.
-
-%%-----------------------------------------------------------
-\subsection{Acknowledgments} 
-In the acknowledgments section, which appears just before the references, the authors may credit others for their guidance or help.
-Also, funding sources or sponsorship information may be stated.
-The acknowledgments section does not have a section number.
+%%%%%Sometimes it is necessary to precede the double slash 
+%%%%%by \verb|\protect| to get the desired result, 
+%%%%%for example, in article titles.
 
@@
 The References section lists books, articles, and reports that are cited in the paper.
-This section does not have a section number.
+It does not have a section number.
 The references are numbered in the order in which they are cited.
@@
 
-The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.
-The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.
+The reference list at the end of this document is created using BibTeX, which looks through the file {\tt report.bib} for the entries cited in the LaTeX source file.
+The format of the reference list is determined by the bibliography style file {\tt spiebib.bst}, as specified in the \verb|\bibliographystyle{spiebib}| command.
 Alternatively, the references may be directly formatted in the LaTeX source file.
 
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.
-Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.
-A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.
+For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors, book title (in italics), page or chapter numbers, publisher, city, and year of publication.
+A reference to a journal article\cite{Metropolis53} includes the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers, and year.
+By convention\cite{Lamport94}, article titles are capitalized as described in Sec.~\ref{sec:title}.
+A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), if appropriate, editors, volume or series title (in italics), volume number (in bold), if applicable, inclusive page numbers, publisher, city, and year.
 References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.
 
-The references are numbered in the order of their first citation.
-Citations to the references are made using superscripts, as demonstrated in the preceding paragraph.
-One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ..."  Two or more references should be separated by a comma with no space between them.
-Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.
-
-%%---------------------------
-\subsubsection{Reference linking and DOIs} 
-A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet.
-The use of DOIs allows readers to easily access cited articles.
-Authors should include the DOI at the end of each reference in brackets, if a DOI is available.
-See examples at the end of this manuscript.
-A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}.
-The inclusion of DOIs will facilitate reference linking and is highly recommended.
-
-In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note" in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}.
-The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.
+Citations to the references are made using superscript numerals, as demonstrated in the preceding paragraph.
+One may also directly refer to a reference within the text, e.g., ``as shown in Ref.~\citenum{Metropolis53} ..."
 
 %%-----------------------------------------------------------
-\subsection{Biographies} 
-A brief professional biography not to exceed 75 words may be provided for each author, if available.
-Biographies should be placed at the end of the paper, after the references.
-Personal information such as hobbies or birthplace/birthdate should not be included.
-Author photographs are not published.
+\subsection{Footnotes} 
+Footnotes\footnote{Footnotes are indicated as superscript symbols to avoid confusion with citations.} may be used to provide auxiliary information that doesn't need to appear in the text, e.g., to explain measurement units.
+They should be used sparingly, however.
+
+Only nine footnote symbols are available in LaTeX.
+If you have more than nine footnotes, you will need to restart the sequence using the command  \verb|\footnote[1]{Your footnote text goes here.}|.
+If you don't, LaTeX will provide the error message {\tt Counter too large.}, followed by the offending footnote command.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Section Formatting} \label{sect:sections}
+\section{SECTION FORMATTING} \label{sec:sections}
 
+Section headings are centered and formatted completely in uppercase 11-point bold font.
+Sections should be numbered sequentially, starting with the first section after the Abstract.
+The heading starts with the section number, followed by a period.
 In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.
-Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references.
-(Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.
 
-Main section headings are in 12-pt., bold font, left-justified and in title case, where important words are capitalized.
-
-Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style.
+Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style\cite{Lamport94}.
 The same goes for leading paragraphs of subsections and sub-subsections.
-Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation.
-There is no additional space between paragraphs.
-In LaTeX, paragraphs are separated by blank lines in the source file.
+Subsequent paragraphs are standard paragraphs, with 14-pt.\ (5 mm) indentation.
+An extra half-line space should be inserted between paragraphs.
+In LaTeX, this spacing is specified by the parameter \verb|\parskip|, which is set in {\tt spie.cls}.
 Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.
@@
 %%-----------------------------------------------------------
-\subsection{Subsection Headings} 
-All important words in a subsection (level 1) header are capitalized.
-Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end.
-The heading is left justified and its font is 12 pt., italic.
+\subsection{Subsection Attributes}
+
+The subsection heading is left justified and set in 11-point, bold font.
+Capitalization rules are the same as those for book titles.
+The first word of a subsection heading is capitalized.
+The remaining words are also capitalized, except for minor words with fewer than four letters, such as articles (a, an, and the), short prepositions (of, at, by, for, in, etc.), and short conjunctions (and, or, as, but, etc.).
+Subsection numbers consist of the section number, followed by a period, and the subsection number within that section.
 
 %%-----------
-\subsubsection{Sub-subsection headings} 
-The first word of a sub-subsection is capitalized.
-The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known).
-The heading is left justified and its font is 11 pt., italic.
+\subsubsection{Sub-subsection attributes} 
+The sub-subsection heading is left justified and its font is 10 point, bold.
+Capitalize as for sentences.
+The first word of a sub-subsection heading is capitalized.
+The rest of the heading is not capitalized, except for acronyms and proper names.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Figures and Tables}
+\section{FIGURES AND TABLES}
 
-%%-----------------------------------------------------------
-\subsection{Figures}
+Figures are numbered in the order of their first citation.
+They should appear in numerical order and on or after the same page as their first reference in the text.
+Alternatively, all figures may be placed at the end of the manuscript, that is, after the Reference section.
+It is preferable to have figures appear at the top or bottom of the page.
+Figures, along with their captions, should be separated from the main text by at least 0.2 in.\ or 5 mm.
 
-Figures are numbered in the order in which they are called out in the text.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It may be necessary to move figures or tables around to enhance readability.
-LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.
+Figure captions are centered below the figure or graph.
+Figure captions start with the figure number in 9-point bold font, followed by a period; the text is in 9-point normal font; for example, ``{\footnotesize{Figure 3.}  Original image...}".
+See Fig.~\ref{fig:example} for an example of a figure caption.
+When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.
 
-Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered.
-Figure captions are centered below the figure or graph.
-Figure captions start with the abbreviation ``Fig" in front of the figure number, followed by a period, and the text in 10-pt.
-font.
-See Fig.~\ref{fig:example} for an example.
-
+Tables are handled identically to figures, except that their captions appear above the table. 
 %%  Use following command to specify that graphics file is in 
@@
 %%  Note use of / to separate subdirectories, for UNIX and Windows OS.
+%%\graphicspath{{H:/HANSON/SPIESTY/}}
+%% tabular environment useful for creating an array of images  
 %-------------
@@
    \begin{tabular}{c}
-   \includegraphics[height=5.5cm]{mcr3b.eps}
+   \includegraphics[height=7cm]{figures/mcr3b.eps}
    \end{tabular}
    \end{center}
-   \caption 
-   { \label{fig:example} %>> use \label inside caption to get Fig. number with \ref{}
-Example of a figure caption. } 
+   \caption[example] 
+%>>>> use \label inside caption to get Fig. number with \ref{}
+   { \label{fig:example} 
+Figure captions are used to describe the figure and help the reader understand it's significance.
+The caption should be centered underneath the figure and set in 9-point font.
+It is preferable for figures and tables to be placed at the top or bottom of the page.
+LaTeX tends to adhere to this standard.}
    \end{figure} 
 %-------------
-Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.
-In no case, should the article's text be wrapped around a figure.
-Figure~\ref{fig:example2} shows two side-by-side images.
-When a figure contains more than one image, the author must submit them as a single image file.
-Further details about figure formatting can be found at \linkable{http://spie.org/x85020.xml
-\#Components}.
 
-%------------- 
-   \begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
-     \\
-     (a) \hspace{5.1cm} (b)
-   \end{tabular}
-   \end{center}
-   \caption 
-   { \label{fig:example2} %>> use \label inside caption to get Fig. number with \ref{}
-Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
-   \end{figure}
-
-%-------------%%-----------------------------------------------------------
-\subsection{Tables} 
-Tables are numbered in the order in which they are referenced.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It is preferable to have tables appear at the top or bottom of the page, if possible.
-Table captions are handled identically to those for figures, except that they appear above the table.
-See Table~\ref{tab:fonts} for an example.
-%%-----------------------------------------------------------
-
-\subsection{Multimedia} 
-Please refer to the multimedia guidelines at \linkable{http://spie.org/x85020.xml\#Multimedia} for specific submission guidelines and requirements.
-The following types of multimedia files are accepted: QuickTime Non-Streaming video (.qt or .mov), MPEG (.mpg or .mp4).
-The recommended maximum size for each multimedia file is 10-12 MB.
-Authors must insert a representative “still” image from the video file in the manuscript as a “figure.” This still image will be linked by the publisher to the actual video file, as will the caption label.
-Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.
-Otherwise  The multimedia file type should be included in parentheses at the end of the figure caption, along with the file size.
-See Video \ref{vid:satellite} for an example.
-
-%-------------
-   \begin{video}
-   \begin{center}
-   {\includegraphics[height=5cm]{satellite.eps}}
-   \\
-   \end{center}
-   \caption{\label{vid:satellite} Example of a multimedia still image (MPEG, 2.5 MB).}
-   \end{video} 
-%-------------
+For further details concerning the inclusion of grayscale and color images, consult SPIE's {\it Author Guide for Publication and Presentation}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Miscellaneous Formatting Details} \label{sect:misc}
+\section{MISCELLANEOUS FORMATTING DETAILS} \label{sec:misc}
 
-At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.
+It is often useful to refer back (or forward) to other sections in the article.
+Such references are made by section number.
+When a section reference starts a sentence, Section is spelled out; otherwise use its abbreviation, for example, ``In Sec.~2 we showed..." or ``Section~2.1 contained a description...".
+References to figures, tables, and theorems are handled the same way.
+
+At the first occurrence of an acronym, spell it out, followed by the acronym in parentheses, e.g., noise power spectrum (NPS).
 
@@
 \subsection{Formatting Equations} 
-Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.
+Equations may appear in line with the text, if they are simple, short, and not of major importance; e.g., $\beta = b/r$.
 Important equations appear on their own line.
 Such equations are centered.
-For example, ``The expression for the field of view is
+For example, ``The expression for the minus-log-posterior is
 	\begin{equation}
-	\label{eq:fov}
-2 a = \frac{(b + 1)}{3c} \, ,
+	\label{eq:alpha}
+\phi = |{\rm\bf y} - {\rm\bf A}{\rm\bf x}|^2 + \alpha \log p({\rm\bf x}) \, ,
 	\end{equation}
-where $a$ is the ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.
+where $\alpha$ determines the strength of ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.
 
 Equations are considered to be part of a sentence and should be punctuated accordingly.
-In the above example, a comma appears after the equation because the next line is a subordinate clause.
+In the above example, a comma follows the equation because the next line is a subordinate clause.
 If the equation ends the sentence, a period should follow the equation.
@@
 
-References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..." Note that the word ``Equation" is spelled out if it begins a sentence, but is abbreviated as ``Eq." otherwise.
-Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq." and the following equation number..
+References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:alpha}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..."  Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks.
 
@@
 
-To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.
-The text of the theorem continues on the same line in normal, 10-pt.
-font, achieved in LaTeX using \verb|\footnotesize|.
+To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified and followed by a period.
+The text of the theorem continues on the same line in normal, 10-point font.
 For example,
 
-\vspace{2ex}\noindent{\footnotesize{\bf Theorem 1.} For any unbiased estimator...}
+\noindent{\bf Theorem 1.} For any unbiased estimator...
+
+Formal statements of lemmas and algorithms receive a similar treatment.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Some LaTeX Guidance} \label{sect:latex}
-
-To work properly, the LaTeX style file {\ttfamily spieman.cls} used to create this document requires following LaTeX packages:
-{\ttfamily times.sty}, {\ttfamily float.sty}, {\ttfamily ifthen.sty}, {\ttfamily setspace.sty}, \\{\ttfamily cite.sty} (version 4.01 or later), and {\ttfamily color.sty}.
-If you do not have them in your LaTeX environment, see your system manager, or download them from \linkable{http://www.ctan.org}.
-
-The author is required to make sure his or her manuscript is properly formatted.
-LaTeX sometimes needs some help to avoid making gross formatting blunders.
-The source file for this document provides examples of how to cope with some of LaTeX's shortcomings.
+\section{SOME LATEX GUIDANCE} \label{sec:latex}
 
@@
 
-Manuscripts submitted for SPIE journals as Portable Document Format (PDF) files must be formatted for US-letter-size paper and have the correct margins.
+Manuscripts submitted electronically to as PostScript (PS) files must have the correct margins.
+LaTeX margins are related to the document's paper size.
+The paper size is set at two separate places in the process of creating a PS file.
+The first place is in {\tt latex}.
+The default in {\tt article.tex}, on which {\tt spie.cls} is based, is USA letter paper.
+To format a document for A4 paper, the first line of the LaTeX source file should be \verb|\documentclass[a4paper]{spie}|.
+
 The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.
+The application DVIPS is typically used to convert the DVI file to a PS file.
+DVIPS has its own default paper size, which can be overridden with the option ``{\tt -t letter}" or ``{\tt -t a4}".
+If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command, for example.
 
-One may directly create a PDF file from the DVI file with the LaTeX utility {\ttfamily dvipdfm}, for example.
-No options are necessary.
-Appealing aspects of this utility are that Acrobat Distiller is not needed, and Type 1 PostScript fonts are automatically included in the resulting PDF file.
-Furthermore, {\ttfamily dvipdfm} allows one to directly incorporate images in JPEG, PNG, and PDF formats, and not just EPS, which is normally used with LaTeX.
-
-Alternatively, with an application such as Adobe Acrobat, PDF files can be created from PostScript (PS) files, which can be produced by DVIPS.
-In most cases, the following DVIPS options should be invoked.
-
-An important DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file.
+Another DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file.
 This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.
-The option ``{\ttfamily -P pdf}" makes DVIPS include these fonts in its output PS file.
-
-LaTeX margins are related to the document's paper size. The paper size is set at two separate places in the process of creating a PS file. The first place is in {\ttfamily latex}. 
-The second place is in the application DVIPS. DVIPS has its own default paper size, which can be overridden with the option ``{\ttfamily -t letter}" or ``{\ttfamily -t a4}".  
-If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command.
-
-The {\ttfamily times.sty} package produces a bug in the handling certain combinations of letters; for example, `fi' is interpretted as a British pound symbol.
-Use the option ``{\ttfamily -G0}" ( capital G and zero) to avoid this problem.
-
-To summarize, the following DVIPS options are recommended when making the PS file: ``{\ttfamily -t letter -P pdf -G0}".
+The option ``{\tt -P pdf}" makes DVIPS include these fonts in its output PS file.
 
@@
 \verb+\usepackage[]{amsmath}+ \\[1ex]
-Then for bold math symbols, use \verb+\boldsymbol+; for example, 
+Then for bold math symbols use \verb+\boldsymbol+ in equations, e.g., 
 \verb+$\boldsymbol{\pi}$+ 
-yields a bold pi.  You can make it easier to use by defining a shorthand command:\\[1ex]
+yields a bold pi.  You can make it easier to use by defining a command:\\[1ex]
 \verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
@@
 Then, in the title, use something like:\\[1ex]
-\verb+\title{Estimation of {$\boldsymbol\alpha$} by a Monte Carlo + \linebreak\verb+technique}+ \\[1ex]
+\verb+\title{Estimation of {\LARGE$\boldsymbol\alpha$} by a Monte Carlo technique}+ \\[1ex]
 Note that the command to create the alpha character is enclosed within braces to form a self-contained environment.
+The use of \verb+\LARGE+ in this example may not be needed when using nondefault font packages, such as the {\tt times} package, because of how the article title is handled in {\tt spie.cls}.
 
 %%-----------------------------------------------------------
-\subsection{Uppercase Letters and Special Symbols in BibTex and LaTeX}
+\subsection{Uppercase letters and special symbols in BibTex}
 
 BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case.
-LaTeX does the same thing for the article title.
 BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.
 
-The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged within braces \verb!{}!.
+The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged in braces.
 Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
@@
 \verb+ author = "S. Kaczmarz",+ \\ 
-\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen + \linebreak\verb+linearer {G}leichungen",+ \\ 
+\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen linearer {G}leichungen",+ \\ 
 \verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
@@
 \verb+ year   = "1937"	} + \\[1ex]
-This example shows the treatment for both umlauts and uppercase letters.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments 
-This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.
+This example shows the use of both umlauts and uppercase letters.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% References %%%%%
-
-\bibliography{report}   %>>>> bibliography data in report.bib
-\bibliographystyle{spiejour}   %>>>> makes bibtex use spiejour.bst
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Biographies of authors %%%%%
-
-\vspace{2ex}\noindent{\bf First Author} is an assistant professor at the University of Optical Engineering.
-He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.
-He is the author of more than 50 journal papers and has written three book chapters.
-His current research interests include optical interconnects, holography, and optoelectronic systems.
-He is a member of SPIE.
-
-\vspace{1ex}
-\noindent Biographies and photographs of the other authors are not available.
-
-\listoffigures
-\listoftables
-
-\end{spacing}
-\end{document}
+\end{comment}

### 2014-11-30 latex-spie/article.tex
Methodology is finished.

@@
 \usepackage{subcaption}
+\usepackage{multirow}
+\usepackage{array}
+\usepackage{tabularx}
+\usepackage{enumerate}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{bbm}
+\usepackage[mathcal]{euscript}
+\usepackage{mathtools}
+
+\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
 
@@
 \section{INTRODUCTION}
-\label{sec:intro}
 
@@
 
-In this paper, we present an enhanced loop closure method based on image-to-image matching in indoor environments with the additional depth information.
+In this paper, we present an enhanced loop closure method based on image-to-image matching with the additional depth information in indoor environments.
 Specifically, we adopt visual place recognition without using any metrical information such as rotation and exact location to correctly identify the previously visited location.
-This technique is quite simple to provide low computational complexity and performs in real-time with high loop closing accuracy.
+This technique is quite simple because of its low computational complexity, and performs in real-time with high loop closing accuracy.
 
@@
 These moments are used to represent shape information inside the image within the context of image processing.
-In this study, the use of CZMs are examined in predefined non-overlapping patches of the image.
-The complex moments
+To make the image description more robust, the ZMs of the input image is calculated in local manner.
+In this study, the ZMs are extracted from both the greyscale and depth images separately and concatenated sequentially to create ultimate feature vector.
+
+The locations are represented with the histograms of their images.
+Detecting loop closing events can be considered as a machine learning problem which number of classes expands continuously when a new unseen location comes.
+We utilized Nearest Neighbour (NN) algorithm to classify locations by which the distance metric is the regular $L_1$ aka.
+Manhattan distance that is one of the simplest distance metric available.
+In other words, the image which distance between the input image is minimum closes the loop, if the distance is lower than the predefined threshold value.
+
+\subsection{Literature Review}
+
+Visual loop closing techniques can be categorized into three main parts\cite{Williams09} : Image-to-image and image-to-map, map-to-map techniques.
+Most of the image-to-image loop closing approaches that rely on considering whole image\cite{Cadena10, Cummins08} .
+
+Loop closure estimations are cast by matching images.
+Most of image-to-image loop closing approaches that rely on salient image regions, utilize small, low-level features like \cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{4633680, CumminsNewmanIJRR08, 5650234, HoNewmanCIRA2005}.
+However, there is a technique that is used to extract relatively larger patches specific to environment that the robot navigates \cite{sariyanidi_iv} on.
+Similar approaches are defined in other studies as well\cite{Espinace:2008:UIU:1377036.1377148, 1570189}, however these techniques do not define a complete loop closing framework.
+
+The Bag of Words\cite{1238663} method has also been widely used to visual place recognition.
+Many notable techniques have been developed after this representation, since it is quite suitable to represent place images and match them on an appearance space.
+The well-known FAB-MAP method proposes a generative probabilistic model\cite{CumminsNewmanIJRR08} which relies on BoW model, and a method to identify new places is proposed.
+The BoW model has also been utilized along with Bayesian Filtering\cite{4633680} to reliably detect the loop closures.
+The BoW model has also used to eliminate the majority of candidates\cite{5650234} and loop closing is decided after geometrically inconsistent matches are discarded using conditional random fields.
+More extensive information related visual loop closure techniques can be found on the relevant survey \cite{williams09}.
 
@@
 \section{METHODOLOGY}
-\label{sec:method}
 
-Methodology will be written here.
+As it has been mentioned earlier, the presented loop closing approach relies on the calculating Zernike Moments of partitioned image blocks across the input image in a local manner.
+
+The whole image representation is constructed as follows.
+Firstly, the ZMs of each subimages that are obtained by partitioning the input image is calculated.
+After that, the calculated complex moments are roughly quantized by keeping only the sign of the real and imaginary components and ignoring the rest of the information.
+Finally, the quantized binary data is coded with histograms that are concatenated to form the final feature vector.
+
+%%% PARTITIONED IMAGE
+\begin{figure}[!htb]
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=3cm]{figures/divided_image.png}    
+        \vspace{3mm}
+        \caption{Image partitioned into blocks by k = 3}
+        \label{fig:divided_image}
+\end{figure}
+
+\subsection{Extraction of Quantized Local Zernike Moments}
+
+The Complex Zernike Moments (ZM) of an image are used to represent the image on the 2-dimensional complex subspace.
+They are extracted using a set of complex polynomials which form a complete orthogonal radial basis functions defined on the unit disc.
+The coefficients in this complex subspace describe the holistic shape information within the image.
+
+The Complex Zernike Moments of an image $f(i,j)$ are calculated as follows:
+
+\begin{equation}
+\label{eq:global_zernike}
+Z_{nm} = \frac{n+1}{\pi}\sum^{N-1}_{i=0}\sum^{N-1}_{j=0}f(i,j)V^\star(\rho_{ij},\theta_{ij})\Delta
+x_i\Delta y_j, \\
+\end{equation}
+where $x_i$, $y_j$ stand for the image coordinates, $\quad\rho_{ij}=\sqrt{x_i^2+y_i^2}$ and $\quad\theta_{ij} = \tan^{-1}\frac{y_j}{x_i}$ are the polar coordinates of the image, $n$ defines the order of the ZM and $m$ stands for the number of repetitions.
+The constraint between $n$ and $m$ is stated that $|m|\leq n$, and $n-|m|$ must be even.
+Therefore, the number of components with respect to moment order $n$ is calculated as follows:
+
+\begin{equation}
+K(n) =
+\begin{cases}
+  \frac{n(n+2)}{4} &\text{if $n$ is even} \\ 
+  \frac{(n+1)^2}{4} &\text{if $n$ is odd}.
+\end{cases}
+\label{eq:num_moms}
+\end{equation}
+
+In order to extract ZMs in local manner, the input image is divided by $k\times k$-sized subimages in which $k$ is a predefined parameter.
+If the image is not divided by $k$ perfectly, the rest of the part is simply ignored.
+The set of images obtained from partitioning are flatten into a  $k^2\times 1$-sized single column by row for more straightforward representation.
+
+Consider that the input image $\mathbf{I}_{p\times q}$ is a combination of subimages $I_{ij}$:
+
+\begin{equation}
+\mathbf{I}_{p\times q} = \begin{bmatrix}
+ I_{11} & \hdots & I_{1Q} \\
+ \vdots & \ddots & \vdots \\
+ I_{P1} & \hdots & I_{PQ} 
+ \end{bmatrix}
+ \longrightarrow
+ \begin{bmatrix}
+ I_{11} \\
+ \vdots \\
+ I_{1Q} \\
+ \vdots \\
+ I_{P1} \\
+ \vdots \\
+ I_{PQ}
+ \end{bmatrix}
+ \label{eq:divided_mat}
+\end{equation}
+where $P=\floor*{^p/_k}$ and $Q=\floor*{^q/_k}$.
+An exemplar input image partitioned into subimages is shown in Figure \ref{fig:divided_image}.
+The $Z_{nm}$ of the input image can be considered as the transformation of the subimages in (\ref{eq:divided_mat}) individually.
+This transform is applied to subimages with all $n$ and $m$ values according to its order.
+Last, the transformed subimages contains a set of complex coefficients are collected into a new matrix such as:
+
+\begin{equation}
+\mathbf{Z} ( \mathbf{I}_{p\times q} )= 
+\begin{bmatrix}
+\mathbf{Z}(I_{11}) \\
+  \vdots \\
+\mathbf{Z}(I_{1Q}) \\
+  \vdots \\
+\mathbf{Z}(I_{P1}) \\
+  \vdots \\
+\mathbf{Z}(I_{PQ}) \\
+ \end{bmatrix} = 
+ \begin{bmatrix}
+Z_{00}(I_{11}) & \hdots & Z_{nm}(I_{11}) \\
+  \vdots  & & \vdots \\
+Z_{00}(I_{1Q}) & \hdots & Z_{nm}(I_{1Q}) \\
+  \vdots  & & \vdots \\
+Z_{00}(I_{P1}) & \hdots & Z_{nm}(I_{P1}) \\
+  \vdots  & & \vdots \\
+Z_{00}(I_{PQ}) & \hdots & Z_{nm}(I_{PQ}) \\
+ \end{bmatrix} = 
+ \begin{bmatrix}
+a_{00}^{11} + \mathbf{i}b_{00}^{11} & \hdots & a_{nm}^{11} + \mathbf{i}b_{nm}^{11} \\
+  \vdots  & & \vdots \\
+a_{00}^{1Q} + \mathbf{i}b_{00}^{1Q} & \hdots & a_{nm}^{1Q} + \mathbf{i}b_{nm}^{1Q} \\
+  \vdots  & & \vdots \\
+a_{00}^{P1} + \mathbf{i}b_{00}^{P1} & \hdots & a_{nm}^{P1} + \mathbf{i}b_{nm}^{P1} \\
+  \vdots  & & \vdots \\
+a_{00}^{PQ} + \mathbf{i}b_{00}^{PQ} & \hdots & a_{nm}^{PQ} + \mathbf{i}b_{nm}^{PQ} \\
+ \end{bmatrix}.
+ \label{eq:lzm_op}
+\end{equation}
+
+Therefore, $k^2\times K(n)$-sized complex coefficient matrix is obtained.
+In order to represent the data more robust and reduce the size of the descriptor vector, a rough quantization takes place at this step.
+First, the complex numbers are decoupled as real and imaginary components, then the sign of each matrix element is taken to binarize the decoupled $k^2\times 2K(n)$-sized matrix as follows:
+
+\begin{equation}
+\mathbf{Z} ( \mathbf{I}_{p\times q} )
+ \longrightarrow
+ \begin{bmatrix}
+a_{00}^{11} & b_{00}^{11} & \hdots & a_{nm}^{11}  & b_{nm}^{11} \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+a_{00}^{1Q} & b_{00}^{1Q} & \hdots & a_{nm}^{1Q}  & b_{nm}^{1Q} \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+a_{00}^{P1} & b_{00}^{P1} & \hdots & a_{nm}^{P1}  & b_{nm}^{P1} \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+a_{00}^{PQ} & b_{00}^{PQ} & \hdots & a_{nm}^{PQ}  & b_{nm}^{PQ} \\
+ \end{bmatrix}
+  \longrightarrow
+  \begin{bmatrix}
+sgn(a_{00}^{11}) & sgn(b_{00}^{11}) & \hdots & sgn(a_{nm}^{11}) & sgn(b_{nm}^{11}) \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+sgn(a_{00}^{1Q}) & sgn(b_{00}^{1Q}) & \hdots & sgn(a_{nm}^{1Q}) & sgn(b_{nm}^{1Q}) \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+sgn(a_{00}^{P1}) & sgn(b_{00}^{P1}) & \hdots & sgn(a_{nm}^{P1}) & sgn(b_{nm}^{P1}) \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+sgn(a_{00}^{PQ}) & sgn(b_{00}^{PQ}) & \hdots & sgn(a_{nm}^{PQ}) & sgn(b_{nm}^{PQ}) \\
+ \end{bmatrix}
+ \label{eq:lzm_binary}
+\end{equation}
+where $sgn(\bullet)$ which is the signum function. According to (\ref{eq:global_zernike}), $Z_{nm}$ with $m = 0$ is omitted since their imaginary components turn out to be constantly equal to zero.
+
+The next step is representing the binary matrix shown in (\ref{eq:lzm_binary}) with histograms.
+Using the binary values for the overall image representation is not a practical solution.
+Describing binary data with histograms are more common solution to obtain the image representation.
+As the methodology described so far, $k^2\times 2K(n)$-sized binary matrix is extracted.
+Each row of this matrix is linearly combined by weighting each of them as a power of $2$.
+Hence the final feature vector $\mathbf{X}$ is obtained as follows:
+
+\begin{equation}
+\mathbf{X} = 
+  \begin{bmatrix}
+2^0sgn(a_{00}^{11}) & 2^1sgn(b_{00}^{11}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{11}) & 2^{2 K(n)-1}sgn(b_{nm}^{11}) \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+2^0sgn(a_{00}^{1Q}) & 2^1sgn(b_{00}^{1Q}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{1Q}) & 2^{2 K(n)-1}sgn(b_{nm}^{1Q}) \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+2^0sgn(a_{00}^{P1}) & 2^1sgn(b_{00}^{P1}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{P1}) & 2^{2 K(n)-1}sgn(b_{nm}^{P1}) \\
+  \vdots  & \vdots & & \vdots  & \vdots\\
+2^0sgn(a_{00}^{PQ}) &2^1sgn(b_{00}^{PQ}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{PQ}) & 2^{2 K(n)-1}sgn(b_{nm}^{PQ}) \\
+ \end{bmatrix}=
+ \begin{bmatrix}
+ x_{1} \\
+ \vdots \\
+ x_{k^2}
+ \end{bmatrix}
+ \label{eq:lzm_coded}
+\end{equation}
+where $x_{i}$ is an integer ranging between $0$ and $2^{2K(n)-1}-1$.
+
+Finally, the input image $I_{p\times q}$ is described with a histogram of length of $2^{2K(n)-1}$.
 
@@
 \section{EXPERIMENTS}
-\label{sec:exper}
 
-Experiments will be written here.
+The method implemented in this paper has been evaluated on three datasets which lighting is different from one another.
 
-Location offset: 100 frames
+\subsection{Benchmark Datasets}
+
+%%% DATASET EXAMPLES
+\begin{figure}[!htb]
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=7cm]{figures/dataset_examples.png}
+        \caption{Dataset examples: (right) bright, (middle) dim, (left) dark}
+        \label{fig:dataset}
+\end{figure}
+
+\subsection{Experimental Setup}
+
+%----------------------------------------------------------------------------------------------------
+% RESULTS
+%----------------------------------------------------------------------------------------------------
+
+\section{RESULTS}
+\label{sec:results}
+
+\subsection{Detection Performance}
+
+\subsection{Real-Time Performance}
 
@@
 
-%%% DATASET EXAMPLES
-\begin{figure}[!htb]
-        \centering
-         % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=7cm]{figures/dataset_examples.png}
-        \caption{Dataset examples: (right) bright, (middle) dim, (left) dark}
-        \label{fig:dataset}
-\end{figure}
-
 %%% BRIGHT PR CURVE
@@
 %----------------------------------------------------------------------------------------------------
+% CONCLUSION AND FUTURE WORK
+%----------------------------------------------------------------------------------------------------
+
+\section{CONCLUSION AND FUTURE WORK}
+
+%----------------------------------------------------------------------------------------------------
 % ACKNOWLEDGEMENTS
@@
 
-Acknowledgements will be written here.
-
 %----------------------------------------------------------------------------------------------------
@@
 
-\bibliography{report}   %>>>> bibliography data in report.bib
-\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst
+\bibliography{report}   % bibliography data in report.bib
+\bibliographystyle{spiebib}
 
@@
 Line breaks are inserted in LaTeX by entering \verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired location.
-
-%%%%%Sometimes it is necessary to precede the double slash 
-%%%%%by \verb|\protect| to get the desired result, 
-%%%%%for example, in article titles.
-
-%%-----------------------------------------------------------
-\subsection{References} 
-The References section lists books, articles, and reports that are cited in the paper.
-It does not have a section number.
-The references are numbered in the order in which they are cited.
-Examples of the format to be followed are given at the end of this document.
-
-The reference list at the end of this document is created using BibTeX, which looks through the file {\tt report.bib} for the entries cited in the LaTeX source file.
-The format of the reference list is determined by the bibliography style file {\tt spiebib.bst}, as specified in the \verb|\bibliographystyle{spiebib}| command.
-Alternatively, the references may be directly formatted in the LaTeX source file.
-
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors, book title (in italics), page or chapter numbers, publisher, city, and year of publication.
-A reference to a journal article\cite{Metropolis53} includes the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers, and year.
-By convention\cite{Lamport94}, article titles are capitalized as described in Sec.~\ref{sec:title}.
-A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), if appropriate, editors, volume or series title (in italics), volume number (in bold), if applicable, inclusive page numbers, publisher, city, and year.
-References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.
-
-Citations to the references are made using superscript numerals, as demonstrated in the preceding paragraph.
-One may also directly refer to a reference within the text, e.g., ``as shown in Ref.~\citenum{Metropolis53} ..."
-
-%%-----------------------------------------------------------
-\subsection{Footnotes} 
-Footnotes\footnote{Footnotes are indicated as superscript symbols to avoid confusion with citations.} may be used to provide auxiliary information that doesn't need to appear in the text, e.g., to explain measurement units.
-They should be used sparingly, however.
-
-Only nine footnote symbols are available in LaTeX.
-If you have more than nine footnotes, you will need to restart the sequence using the command  \verb|\footnote[1]{Your footnote text goes here.}|.
-If you don't, LaTeX will provide the error message {\tt Counter too large.}, followed by the offending footnote command.
 

### 2014-11-30 latex-spie/article.tex
Benchmark dataset keywords are added

@@
 
-The method implemented in this paper has been evaluated on three datasets which lighting is different from one another.
+The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from one another.
 
 \subsection{Benchmark Datasets}
+
+manually annotated
+Moving platform,
+indoor
+Kinect (grayscale and depth images) 
+Kinect: max line of sight is 10m
+Average speed is approx 0.5 m/s 
+bright, dim, dark (to evaluate depth info)
+bright 2082, dim 2083, dark 2251
+approx 1000 frames per loop
+2 loops, each dataset approx 2000 frames
+1 loop for loop closure testing
+examples shown in \ref{fig:dataset}
 
@@
 \end{figure}
-
-\subsection{Experimental Setup}
 

### 2014-11-30 latex-spie/article.tex
minor changes

--- 2014-11-30 latex-spie/article.tex
@@
 
-The method implemented in this paper has been evaluated on three datasets which lighting is different from one another.
+The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from one another.
 
 \subsection{Benchmark Datasets}
+
+manually annotated, each frame is considered as a different location, similar frame sensitivity is approx 10 frame.
+Moving platform,
+indoor
+Kinect (grayscale and depth images) 
+Kinect: max line of sight is 10m
+Average speed is approx 0.5 m/s 
+bright, dim, dark (to evaluate depth info)
+bright 2082, dim 2083, dark 2251
+approx 1000 frames per loop
+2 loops, each dataset approx 2000 frames
+1 loop for loop closure testing
+examples shown in \ref{fig:dataset}
 

### 2014-11-30 latex-spie/article.tex
test

--- 2014-11-30 latex-spie/article.tex
@@
 Information that is gathered from various data sources including LIDARs, RADARs, stereo       and monocular cameras is highly utilized in loop closure detection.
-With the recent development of visual sensor technologies, the loop closure detection becomes a problem that is open for research in the field of computer vision.
+With the recent development of visual sensor technologies, the loop closure detection became a problem that is open for research in the field of computer vision.
 
@@
 
-As it has been mentioned earlier, the presented loop closing approach relies on the calculating Zernike Moments of partitioned image blocks across the input image in a local manner.
+As it was mentioned earlier, the presented loop closing approach relies on calculating the Zernike Moments of partitioned image blocks across the input image in a local manner.
 
 The whole image representation is constructed as follows.
-Firstly, the ZMs of each subimages that are obtained by partitioning the input image is calculated.
-After that, the calculated complex moments are roughly quantized by keeping only the sign of the real and imaginary components and ignoring the rest of the information.
-Finally, the quantized binary data is coded with histograms that are concatenated to form the final feature vector.
+Firstly, the ZMs of each subimage that were obtained by partitioning the input image is calculated.
+After that, the calculated complex moments are coarsely quantized by keeping only the sign of the real and imaginary components and ignoring the rest of the information.
+Finally, the quantized binary data is coded as histograms that are concatenated to form the final feature vector.
 
@@
 
-In order to extract ZMs in local manner, the input image is divided by $k\times k$-sized subimages in which $k$ is a predefined parameter.
+In order to extract ZMs in local manner, the input image is divided by $k\times k$-sized subimages in which $k$ is a predefined partitioning parameter.
 If the image is not divided by $k$ perfectly, the rest of the part is simply ignored.
-The set of images obtained from partitioning are flatten into a  $k^2\times 1$-sized single column by row for more straightforward representation.
+The set of images obtained from partitioning are flatten into a  $k^2\times 1$-sized single column in row-major order for more straightforward representation.
 
@@
 This transform is applied to subimages with all $n$ and $m$ values according to its order.
-Last, the transformed subimages contains a set of complex coefficients are collected into a new matrix such as:
+Lastly, the transformed subimages contains a set of complex coefficients are collected into a new matrix such as:
 
@@
 Therefore, $k^2\times K(n)$-sized complex coefficient matrix is obtained.
-In order to represent the data more robust and reduce the size of the descriptor vector, a rough quantization takes place at this step.
+In order to facilitate the representation of the data and to reduce the size of the descriptor vector, a coarse quantization takes place at this step.
 First, the complex numbers are decoupled as real and imaginary components, then the sign of each matrix element is taken to binarize the decoupled $k^2\times 2K(n)$-sized matrix as follows:
@@
 \end{equation}
-where $sgn(\bullet)$ which is the signum function. According to (\ref{eq:global_zernike}), $Z_{nm}$ with $m = 0$ is omitted since their imaginary components turn out to be constantly equal to zero.
+where $sgn(\bullet)$ is the signum function. According to (\ref{eq:global_zernike}), $Z_{nm}$ with $m = 0$ is omitted since their imaginary components turn out to be constantly equal to zero.
 
@@
   \begin{bmatrix}
-2^0sgn(a_{00}^{11}) & 2^1sgn(b_{00}^{11}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{11}) & 2^{2 K(n)-1}sgn(b_{nm}^{11}) \\
+sgn(a_{00}^{11}) & sgn(b_{00}^{11}) & \hdots & sgn(a_{nm}^{11}) & sgn(b_{nm}^{11}) \\
   \vdots  & \vdots & & \vdots  & \vdots\\
-2^0sgn(a_{00}^{1Q}) & 2^1sgn(b_{00}^{1Q}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{1Q}) & 2^{2 K(n)-1}sgn(b_{nm}^{1Q}) \\
+sgn(a_{00}^{1Q}) & sgn(b_{00}^{1Q}) & \hdots & sgn(a_{nm}^{1Q}) & sgn(b_{nm}^{1Q}) \\
   \vdots  & \vdots & & \vdots  & \vdots\\
-2^0sgn(a_{00}^{P1}) & 2^1sgn(b_{00}^{P1}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{P1}) & 2^{2 K(n)-1}sgn(b_{nm}^{P1}) \\
+sgn(a_{00}^{P1}) & sgn(b_{00}^{P1}) & \hdots & sgn(a_{nm}^{P1}) & sgn(b_{nm}^{P1}) \\
   \vdots  & \vdots & & \vdots  & \vdots\\
-2^0sgn(a_{00}^{PQ}) &2^1sgn(b_{00}^{PQ}) & \hdots & 2^{2 K(n)-2}sgn(a_{nm}^{PQ}) & 2^{2 K(n)-1}sgn(b_{nm}^{PQ}) \\
+sgn(a_{00}^{PQ}) &sgn(b_{00}^{PQ}) & \hdots & sgn(a_{nm}^{PQ}) & sgn(b_{nm}^{PQ}) \\
+ \end{bmatrix}
+ \begin{bmatrix}
+2^0 \\
+2^1 \\
+ \vdots \\
+  \vdots \\
+   \vdots \\
+ 2^{2 K(n)-2} \\
+ 2^{2 K(n)-1}
  \end{bmatrix}=
  \begin{bmatrix}
- x_{1} \\
+ x_{11} \\
  \vdots \\
- x_{k^2}
+ x_{1Q} \\
+  \vdots \\
+ x_{P1} \\
+  \vdots \\
+ x_{PQ} \\
  \end{bmatrix}
@@
 
-The method implemented in this paper has been evaluated on three datasets which lighting is different from one another.
+The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other.
+
+tested with k = 5, n = 2 ZM parameters
+k x k is the number of regions the input image is divided
+n: the order of ZM
+tested in three different datasets by using image only, depth only and both image and depth.
+image and depth is created by concatenated with image and depth ZM feature vectors
 
 \subsection{Benchmark Datasets}
+
+In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in indoor environment by using Kinect sensor which can grab both RGB and depth images at the same time.
+The lighting conditions in the datasets are sequentially bright, dim and dark in which both depth and RGB images are captured.
+The exemplary images belong to different datasets are shown in Figure \ref{fig:dataset}.
+In some cases, the line of sight of the Kinect is not enough to capture the depth information for $10m$ above distances, thus some of the depth images are decomposed.
+
+Images are collected via Kinect mounted moving platform and approximately pointed in the direction of the displacement with average speed $0.25m/s$.
+Also, the rectangle-shaped trajectory of the three datasets is nearly the same as the others to compare their performances.
+There are two loops that contains 1000 frames per loop for each dataset, one for discovering, the other for evaluating.
+
+manually annotated, each frame is considered as a different location, similar frame sensitivity is approx 10 frame.
 

### 2014-11-30 latex-spie/article.tex
Benchmark datasets are added

@@
 %%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
-%% \addtolength{\voffset}{9mm}   %>>> moves text field down
-%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
 \usepackage[]{graphicx}
@@
 \DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
+%\renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
+%\addtolength{\voffset}{9mm}   %>>> moves text field down
 
@@
 \supit{a}Istanbul Technical University Mechatronics Engineering Department, Maslak 34469, Istanbul, Turkey; 
-\supit{b}Queen Mary University of London School of Electronic Engineering and Computer Science, ADDRESS, London, England; 
+\supit{b}Centre of Intelligent Sensing, Mile End Road, E1 4NS, London, U.K.;
 \supit{c}Istanbul Technical University Control and Automation Engineering Department, Maslak 34469, Istanbul, Turkey
@@
 This transform is applied to subimages with all $n$ and $m$ values according to its order.
-Lastly, the transformed subimages contains a set of complex coefficients are collected into a new matrix such as:
+Lastly, the ZMs computed from transformed subimages are collected into a new matrix as follows:
 
@@
 \mathbf{Z}(I_{PQ}) \\
- \end{bmatrix} = 
+ \end{bmatrix}
+ \longrightarrow
  \begin{bmatrix}
@@
 
-Images are collected via Kinect mounted moving platform and approximately pointed in the direction of the displacement with average speed $0.25m/s$.
-Also, the rectangle-shaped trajectory of the three datasets is nearly the same as the others to compare their performances.
-There are two loops that contains 1000 frames per loop for each dataset, one for discovering, the other for evaluating.
-
-manually annotated, each frame is considered as a different location, similar frame sensitivity is approx 10 frame.
+The images in the datasets are acquired via Kinect mounted moving platform and pointed in the direction of the displacement with average speed $0.25$ m/s.
+Also, the rectangle-shaped trajectory of the three datasets is nearly the same as the others to compare their performances correctly.
+There are two loops that contains 1000 frames per loop in each dataset, one is used for discovering and the other one for evaluating.
+To create the ground truth, the locations which corresponds to approximately 10 sequential frames is annotated manually.
 
@@
         \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=7cm]{figures/dataset_examples.png}
-        \caption{Dataset examples: (right) bright, (middle) dim, (left) dark}
+        \vspace{2mm}
+        \caption{Examplary images belong to benchmark datasets in different lighting conditions which are bright (left), dim (middle) and dark (right).}
         \label{fig:dataset}

### 2014-11-30 latex-spie/article.tex
Introduction is almost finished

@@
 Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location.
+The algorithm is tested in three different datasets which lighting conditions are different from each other.
+Additional depth information beside the actual image increases the detection rate especially in dark.
 \end{abstract}
@@
 In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
-One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM) which still remains as an assertive problem in a lot of ways.
+One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM)\cite{CumminsNewmanIJRR08} which still remains as an assertive problem in a lot of ways.
 Loop closing is defined as the correct identification of previously visited location in terms of SLAM.
-Information that is gathered from various data sources including LIDARs, RADARs, stereo       and monocular cameras is highly utilized in loop closure detection.
+Information that is gathered from various data sources including LIDARs, RADARs, stereo and monocular cameras\cite{williams08iros, 5650234} is highly utilized in loop closure detection.
 With the recent development of visual sensor technologies, the loop closure detection became a problem that is open for research in the field of computer vision.
+
+Visual loop closing techniques can be categorized into three main parts\cite{Williams09}: Image-to-image and image-to-map, map-to-map techniques.
+Loop closure estimations\cite{sariyanidi_spie13}  are cast by matching images.
+Most of image-to-image techniques that rely on salient image patches, used small, low-level features such as \cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{sariyanidi_iv, HoNewmanCIRA2005}.
+One of the widely used methods in visual place recognition problem is the Bag of Words\cite{1238663} method.
+More information related to visual loop closing approaches can be found on the relevant survey \cite{Williams09}.
 
@@
 
-\subsection{Literature Review}
-
-Visual loop closing techniques can be categorized into three main parts\cite{Williams09} : Image-to-image and image-to-map, map-to-map techniques.
-Most of the image-to-image loop closing approaches that rely on considering whole image\cite{Cadena10, Cummins08} .
-
-Loop closure estimations are cast by matching images.
-Most of image-to-image loop closing approaches that rely on salient image regions, utilize small, low-level features like \cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{4633680, CumminsNewmanIJRR08, 5650234, HoNewmanCIRA2005}.
-However, there is a technique that is used to extract relatively larger patches specific to environment that the robot navigates \cite{sariyanidi_iv} on.
-Similar approaches are defined in other studies as well\cite{Espinace:2008:UIU:1377036.1377148, 1570189}, however these techniques do not define a complete loop closing framework.
-
-The Bag of Words\cite{1238663} method has also been widely used to visual place recognition.
-Many notable techniques have been developed after this representation, since it is quite suitable to represent place images and match them on an appearance space.
-The well-known FAB-MAP method proposes a generative probabilistic model\cite{CumminsNewmanIJRR08} which relies on BoW model, and a method to identify new places is proposed.
-The BoW model has also been utilized along with Bayesian Filtering\cite{4633680} to reliably detect the loop closures.
-The BoW model has also used to eliminate the majority of candidates\cite{5650234} and loop closing is decided after geometrically inconsistent matches are discarded using conditional random fields.
-More extensive information related visual loop closure techniques can be found on the relevant survey \cite{williams09}.
+In the next sections, a brief introduction about the methodology is explained first. After that, the experiments and datasets are shown, and finally results are presented.
 

### 2014-11-30 latex-spie/article.tex
Introduction is finished

@@
 
-In the next sections, a brief introduction about the methodology is explained first. After that, the experiments and datasets are shown, and finally results are presented.
+In the following sections, a brief introduction about the methodology is explained first, and then the experiments and datasets are shown, and finally results are presented.
 
@@
 
-In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in indoor environment by using Kinect sensor which can grab both RGB and depth images at the same time.
-The lighting conditions in the datasets are sequentially bright, dim and dark in which both depth and RGB images are captured.
-The exemplary images belong to different datasets are shown in Figure \ref{fig:dataset}.
-In some cases, the line of sight of the Kinect is not enough to capture the depth information for $10m$ above distances, thus some of the depth images are decomposed.
+In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in an indoor environment by using Kinect sensor which can grab both RGB and depth images at the same time.
+The lighting conditions in the datasets are bright, dim and dark in which both depth and RGB images are captured.
+The exemplary images belonging to different datasets are shown in Figure \ref{fig:dataset}.
+In some cases, the line of sight of the Kinect is not enough to capture the depth information for distances above $10m$.
+Thus, some of the depth images are unreliable.
 
-The images in the datasets are acquired via Kinect mounted moving platform and pointed in the direction of the displacement with average speed $0.25$ m/s.
-Also, the rectangle-shaped trajectory of the three datasets is nearly the same as the others to compare their performances correctly.
-There are two loops that contains 1000 frames per loop in each dataset, one is used for discovering and the other one for evaluating.
-To create the ground truth, the locations which corresponds to approximately 10 sequential frames is annotated manually.
+The images in the datasets are acquired via Kinect mounted moving platform and pointed in the direction of the displacement with approximate speed 0.25m/s.
+Also, the rectangle-shaped trajectory of the three datasets is almost the same as the others to compare their performances correctly.
+There are two loops that contain around 1000 frames per loop in each dataset, first one is used for discovering and the second for evaluating.
+To create the ground truth, the locations which corresponds to approximately 10 sequential frames are annotated manually.
 
-%%% DATASET EXAMPLES
+% DISTANCE MATRICES
 \begin{figure}[!htb]
         \centering
+
+        %%% BRIGHT DISTANCE MATRIX
+        \begin{subfigure}[b]{0.27\textwidth}
+        \centering
          % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=7cm]{figures/dataset_examples.png}
-        \vspace{2mm}
-        \caption{Examplary images belong to benchmark datasets in different lighting conditions which are bright (left), dim (middle) and dark (right).}
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_bright.png}    
+        \caption{Bright}
+        \label{subfig:dataset_bright}
+        \end{subfigure}
+        ~ 
+        %%% DIM DISTANCE MATRIX
+        \begin{subfigure}[b]{0.27\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_dim.png}    
+        \caption{Dim}
+        \label{subfig:dataset_dim}
+        \end{subfigure}
+         ~ 
+        %%% DARK DISTANCE MATRIX
+        \begin{subfigure}[b]{0.27\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dataset_dark.png}    
+        \caption{Dark}
+        \label{subfig:dataset_dark}
+        \end{subfigure}
+
+        \hspace{-5mm}
+        \caption{Examplary images belonging to benchmark datasets in different lighting conditions.}
         \label{fig:dataset}

### 2014-12-01 latex-spie/article.tex
Methodology is changed ??

@@
 
+\setcounter{MaxMatrixCols}{14}
 \DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
@@
 In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
-One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM)\cite{CumminsNewmanIJRR08} which still remains as an assertive problem in a lot of ways.
+One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM) which still remains as an assertive problem in a lot of ways.
 Loop closing is defined as the correct identification of previously visited location in terms of SLAM.
@@
 Loop closure estimations\cite{sariyanidi_spie13}  are cast by matching images.
-Most of image-to-image techniques that rely on salient image patches, used small, low-level features such as \cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{sariyanidi_iv, HoNewmanCIRA2005}.
+Most of image-to-image techniques that rely on salient image patches, use small, low-level features such as SURF\cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{sariyanidi_iv, HoNewmanCIRA2005, CumminsNewmanIJRR08}.
 One of the widely used methods in visual place recognition problem is the Bag of Words\cite{1238663} method.
-More information related to visual loop closing approaches can be found on the relevant survey \cite{Williams09}.
+Also, there are some studies that uses additional depth information\cite{kerl2013-IROS} in loop closure problems.More information related to visual loop closing approaches can be found on the relevant survey \cite{Williams09}.
 
@@
 After that, the calculated complex moments are coarsely quantized by keeping only the sign of the real and imaginary components and ignoring the rest of the information.
-Finally, the quantized binary data is coded as histograms that are concatenated to form the final feature vector.
+Next, the quantized binary data is combined linearly by weighting each of them to convert them into integers.
+Finally, the integers values are coded as histograms.
 
@@
 If the image is not divided by $k$ perfectly, the rest of the part is simply ignored.
-The set of images obtained from partitioning are flatten into a  $k^2\times 1$-sized single column in row-major order for more straightforward representation.
 
 Consider that the input image $\mathbf{I}_{p\times q}$ is a combination of subimages $I_{ij}$:
-
 \begin{equation}
@@
  I_{P1} & \hdots & I_{PQ} 
- \end{bmatrix}
- \longrightarrow
- \begin{bmatrix}
- I_{11} \\
- \vdots \\
- I_{1Q} \\
- \vdots \\
- I_{P1} \\
- \vdots \\
- I_{PQ}
- \end{bmatrix}
+ \end{bmatrix},
  \label{eq:divided_mat}
@@
 Lastly, the ZMs computed from transformed subimages are collected into a new matrix as follows:
-
 \begin{equation}
@@
 \begin{bmatrix}
-\mathbf{Z}(I_{11}) \\
-  \vdots \\
-\mathbf{Z}(I_{1Q}) \\
-  \vdots \\
-\mathbf{Z}(I_{P1}) \\
-  \vdots \\
-\mathbf{Z}(I_{PQ}) \\
+\mathbf{Z}(I_{11}) & \hdots & \mathbf{Z}(I_{1Q}) \\
+\vdots & \ddots & \vdots \\
+\mathbf{Z}(I_{P1}) & \hdots & \mathbf{Z}(I_{PQ})
  \end{bmatrix}
@@
  \begin{bmatrix}
-Z_{00}(I_{11}) & \hdots & Z_{nm}(I_{11}) \\
-  \vdots  & & \vdots \\
-Z_{00}(I_{1Q}) & \hdots & Z_{nm}(I_{1Q}) \\
-  \vdots  & & \vdots \\
-Z_{00}(I_{P1}) & \hdots & Z_{nm}(I_{P1}) \\
-  \vdots  & & \vdots \\
-Z_{00}(I_{PQ}) & \hdots & Z_{nm}(I_{PQ}) \\
- \end{bmatrix} = 
- \begin{bmatrix}
-a_{00}^{11} + \mathbf{i}b_{00}^{11} & \hdots & a_{nm}^{11} + \mathbf{i}b_{nm}^{11} \\
-  \vdots  & & \vdots \\
-a_{00}^{1Q} + \mathbf{i}b_{00}^{1Q} & \hdots & a_{nm}^{1Q} + \mathbf{i}b_{nm}^{1Q} \\
-  \vdots  & & \vdots \\
-a_{00}^{P1} + \mathbf{i}b_{00}^{P1} & \hdots & a_{nm}^{P1} + \mathbf{i}b_{nm}^{P1} \\
-  \vdots  & & \vdots \\
-a_{00}^{PQ} + \mathbf{i}b_{00}^{PQ} & \hdots & a_{nm}^{PQ} + \mathbf{i}b_{nm}^{PQ} \\
- \end{bmatrix}.
+Z_{00}(I_{11}) & \hdots & Z_{nm}(I_{11}) & \hdots & Z_{00}(I_{1Q}) & \hdots & Z_{nm}(I_{1Q}) \\
+\vdots & \ddots & \vdots & & \vdots & \ddots & \vdots  \\
+Z_{00}(I_{P1}) & \hdots & Z_{nm}(I_{P1}) & \hdots & Z_{00}(I_{PQ}) & \hdots & Z_{nm}(I_{PQ}) \\
+ \end{bmatrix},
  \label{eq:lzm_op}
 \end{equation}
-
-Therefore, $k^2\times K(n)$-sized complex coefficient matrix is obtained.
-In order to facilitate the representation of the data and to reduce the size of the descriptor vector, a coarse quantization takes place at this step.
-First, the complex numbers are decoupled as real and imaginary components, then the sign of each matrix element is taken to binarize the decoupled $k^2\times 2K(n)$-sized matrix as follows:
 
@@
  \begin{bmatrix}
-a_{00}^{11} & b_{00}^{11} & \hdots & a_{nm}^{11}  & b_{nm}^{11} \\
-  \vdots  & \vdots & & \vdots  & \vdots\\
-a_{00}^{1Q} & b_{00}^{1Q} & \hdots & a_{nm}^{1Q}  & b_{nm}^{1Q} \\
-  \vdots  & \vdots & & \vdots  & \vdots\\
-a_{00}^{P1} & b_{00}^{P1} & \hdots & a_{nm}^{P1}  & b_{nm}^{P1} \\
-  \vdots  & \vdots & & \vdots  & \vdots\\
-a_{00}^{PQ} & b_{00}^{PQ} & \hdots & a_{nm}^{PQ}  & b_{nm}^{PQ} \\
- \end{bmatrix}
+a_{00}^{11} + \mathbf{i}b_{00}^{11} & \hdots & a_{nm}^{11} + \mathbf{i}b_{nm}^{11} & \hdots &  a_{00}^{1Q} + \mathbf{i}b_{00}^{1Q} & \hdots & a_{nm}^{1Q} + \mathbf{i}b_{nm}^{1Q} \\
+\vdots & \ddots & \vdots & & \vdots & \ddots & \vdots  \\
+a_{00}^{P1} + \mathbf{i}b_{00}^{P1} & \hdots & a_{nm}^{P1} + \mathbf{i}b_{nm}^{P1} & \hdots & a_{00}^{PQ} + \mathbf{i}b_{00}^{PQ} & \hdots & a_{nm}^{PQ} + \mathbf{i}b_{nm}^{PQ} \\
+ \end{bmatrix}.
+\end{equation}
+
+Therefore, $k\times kK(n)$-sized complex coefficient matrix is obtained.
+In order to facilitate the representation of the data and to reduce the size of the descriptor vector, a coarse quantization takes place at this step.
+First, the complex numbers are decoupled as real and imaginary components, then the sign of each matrix element is taken to binarize the decoupled $k\times 2kK(n)$-sized matrix as follows:
+
+\begin{equation}
+\mathbf{Z} ( \mathbf{I}_{p\times q} )
  \longrightarrow
  \begin{bmatrix}
-sgn(a_{00}^{11}) & sgn(b_{00}^{11}) & \hdots & sgn(a_{nm}^{11}) & sgn(b_{nm}^{11}) \\
-  \vdots  & \vdots & & \vdots  & \vdots\\
-sgn(a_{00}^{1Q}) & sgn(b_{00}^{1Q}) & \hdots & sgn(a_{nm}^{1Q}) & sgn(b_{nm}^{1Q}) \\
-  \vdots  & \vdots & & \vdots  & \vdots\\
-sgn(a_{00}^{P1}) & sgn(b_{00}^{P1}) & \hdots & sgn(a_{nm}^{P1}) & sgn(b_{nm}^{P1}) \\
-  \vdots  & \vdots & & \vdots  & \vdots\\
-sgn(a_{00}^{PQ}) & sgn(b_{00}^{PQ}) & \hdots & sgn(a_{nm}^{PQ}) & sgn(b_{nm}^{PQ}) \\
+a_{00}^{11} & b_{00}^{11} & \hdots & a_{nm}^{11} & b_{nm}^{11} & \hdots &  a_{00}^{1Q} & b_{00}^{1Q} & \hdots & a_{nm}^{1Q} & b_{nm}^{1Q} \\
+\vdots & \vdots & \ddots & \vdots & \vdots &  & \vdots & \vdots & \ddots & \vdots & \vdots \\
+a_{00}^{P1} & b_{00}^{P1} & \hdots & a_{nm}^{P1} & b_{nm}^{P1} & \hdots &  a_{00}^{PQ} & b_{00}^{PQ} & \hdots & a_{nm}^{PQ} & b_{nm}^{PQ}
  \end{bmatrix}
- \label{eq:lzm_binary}
+  \label{eq:lzm_decoupled}
 \end{equation}
-where $sgn(\bullet)$ is the signum function. According to (\ref{eq:global_zernike}), $Z_{nm}$ with $m = 0$ is omitted since their imaginary components turn out to be constantly equal to zero.
 
-The next step is representing the binary matrix shown in (\ref{eq:lzm_binary}) with histograms.
+\begin{equation}
+\mathbf{Z} ( \mathbf{I}_{p\times q} )
+ \longrightarrow
+ \begin{bmatrix}
+s(a_{00}^{11}) & s(b_{00}^{11}) & \hdots & s(a_{nm}^{11}) & s(b_{nm}^{11}) & \hdots & s(a_{00}^{1Q}) & s(b_{00}^{1Q}) & \hdots & s(a_{nm}^{1Q}) & s(b_{nm}^{1Q}) \\
+\vdots & \vdots & \ddots & \vdots & \vdots & & \vdots & \vdots & \ddots & \vdots & \vdots \\
+s(a_{00}^{P1}) & s(b_{00}^{P1}) & \hdots & s(a_{nm}^{P1}) & s(b_{nm}^{P1}) & \hdots &  s(a_{00}^{PQ}) & s(b_{00}^{PQ}) & \hdots & s(a_{nm}^{PQ}) & s(b_{nm}^{PQ})
+ \end{bmatrix}
+  \label{eq:lzm_sign}
+\end{equation}
+where $s(\bullet) \equiv sgn(\bullet)$ which is the signum function.
+According to (\ref{eq:global_zernike}), $Z_{nm}$ with $m = 0$ is omitted since their imaginary components turn out to be constantly equal to zero.
+
+The next step is representing the binary matrix shown in (\ref{eq:lzm_sign}) with histograms.
 Using the binary values for the overall image representation is not a practical solution.
 Describing binary data with histograms are more common solution to obtain the image representation.
-As the methodology described so far, $k^2\times 2K(n)$-sized binary matrix is extracted.
+As the methodology described so far, $k\times 2kK(n)$-sized binary matrix is extracted.
 Each row of this matrix is linearly combined by weighting each of them as a power of $2$.

### 2014-12-01 latex-spie/article.tex
Methodology is finished git push

--- 2014-11-30 latex-spie/article.tex
@@
 Each row of this matrix is linearly combined by weighting each of them as a power of $2$.
-Hence the final feature vector $\mathbf{X}$ is obtained as follows:
+Hence a column vector $\mathbf{C}$ is obtained with integer values ranging between $0$ and $2^{2K(n)-1}-1$:
 
 \begin{equation}
-\mathbf{X} = 
+\mathbf{C} = 
+\begin{bmatrix}
+c_{j}
+\end{bmatrix}=
   \begin{bmatrix}
@@
  2^{2 K(n)-1}
- \end{bmatrix}=
- \begin{bmatrix}
- x_{11} \\
- \vdots \\
- x_{1Q} \\
-  \vdots \\
- x_{P1} \\
-  \vdots \\
- x_{PQ} \\
  \end{bmatrix}
@@
 \end{equation}
-where $x_{i}$ is an integer ranging between $0$ and $2^{2K(n)-1}-1$.
 
-Finally, the input image $I_{p\times q}$ is described with a histogram of length of $2^{2K(n)-1}$.
+Finally, the histogram is defined that consists of $2^{2K(n)-1}$ bins, and each bin is filled with the number of occurrences of the integers in $\mathbf{C}$.
+Therefore, the input image $I_{p\times q}$ is described with a histogram of length of $2^{2K(n)-1}$.
 

### 2014-12-01 latex-spie/article.tex
Eperiments is finished

@@
 Detecting loop closing events can be considered as a machine learning problem which number of classes expands continuously when a new unseen location comes.
-We utilized Nearest Neighbour (NN) algorithm to classify locations by which the distance metric is the regular $L_1$ aka.
+We utilized Nearest Neighbour (NN) algorithm to classify locations by which the distance metric is the regular $L_1$ a.k.a.
 Manhattan distance that is one of the simplest distance metric available.
@@
 \section{METHODOLOGY}
+\label{sec:method}
 
@@
 The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other.
+The tests are done with either using gray and depth images separately or using both of them.
+After that, the difference matrices are calculated to examine the results.
+Nearest Neighbour (NN) algorithm is utilized to classify the new locations and the distance metric is $L_{1}$.
 
-tested with k = 5, n = 2 ZM parameters
-k x k is the number of regions the input image is divided
-n: the order of ZM
-tested in three different datasets by using image only, depth only and both image and depth.
-image and depth is created by concatenated with image and depth ZM feature vectors
+The method described in Section \ref{sec:method} has basically two parameters that must be adjusted.
+One of them is $k\times k$ the size of subimages that the input image partitioned by in (\ref{eq:divided_mat}) and the other one is $n$ the order of the Zernike polynomials.
+During the experiments, the parameter set is selected as $k=30$ and $n=2$.
+Then the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions.
+The histograms of each subregion are simply concatenated to compose the feature vector of an image.
+In order to construct the ultimate feature vector containing both gray and depth images, each feature vectors obtained from both images are also concatenated.
 
@@
 
-% DISTANCE MATRICES
+% BENCHMARK DATASETS
 \begin{figure}[!htb]
@@
 
-        %%% BRIGHT DISTANCE MATRIX
+        %%% BRIGHT 
         \begin{subfigure}[b]{0.27\textwidth}
@@
         ~ 
-        %%% DIM DISTANCE MATRIX
+        %%% DIM 
         \begin{subfigure}[b]{0.27\textwidth}
@@
          ~ 
-        %%% DARK DISTANCE MATRIX
+        %%% DARK
         \begin{subfigure}[b]{0.27\textwidth}
@@
 
-        \hspace{-5mm}
+        \hspace{-3mm}
         \caption{Examplary images belonging to benchmark datasets in different lighting conditions.}
@@
 
-%%% BRIGHT PR CURVE
+% RESULTS
 \begin{figure}[!htb]
         \centering
-         % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_bright.eps}    
-        \caption{Bright dataset results}
-        \label{fig:pr_bright}
-\end{figure}
 
-%%% DIM PR CURVE
-\begin{figure}[!htb]
+        %%% BRIGHT PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
         \centering
          % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_dim.eps}    
-        \caption{Dim dataset results}
-        \label{fig:pr_dim}
-\end{figure}
-
-%%% DARK PR CURVE
-\begin{figure}[!htb]
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
+        \caption{Bright dataset results.}
+        \label{subfig:pr_bright}
+        \end{subfigure}
+        ~ 
+        %%% DIM PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
         \centering
          % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=8cm]{figures/pr_dark.eps}      
-        \caption{Dark dataset results}
-        \label{fig:pr_dark}
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
+        \caption{Dim dataset results.}
+        \label{subfig:pr_dim}
+        \end{subfigure}
+        ~
+        %%% DARK PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
+        \caption{Dark dataset results.}
+        \label{subfig:pr_bright}
+        \end{subfigure}
+        ~ 
+        %%% ALL PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
+        \caption{Comparison between datasets.}
+        \label{subfig:pr_dim}
+        \end{subfigure}
+
+        \hspace{-3mm}
+        \caption{PR curves}
+        \label{fig:pr_curves}
 \end{figure}

### 2014-12-01 latex-spie/article.tex
Change in abstract

@@
 \begin{abstract}
-Visual loop closure detection problem is an active area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
-In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction with saliency detection technique.
-In contradistinction to the previous methods, our approach uses additional depth information.
-Saliency regions are used to refer to the certain distinctive areas on the image patches.
-They are also suitable to represent locations in a sparse manner.
-In order to find out the similarity between two locations we use a straightforward function, that contains the detection confidences of the image and the landmark coordinates in 3D.
-Recognition of the previously visited and unvisited locations is also considered in the framework.
-Exemplary results and the practical implementation of the method are also given with the data gathered on the testbed with a depth camera (Kinect) mounted differential drive autonomous ground vehicle.
-Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location.
-The algorithm is tested in three different datasets which lighting conditions are different from each other.
+Visual loop closure detection problem is an active research area for indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
+In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction by means of quantized local Zernike moments.
+In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike moments.
+Zernike transform is an effective tool for referring to the certain distinctive areas on the image patches.
+Therefore, it is a suitable method to represent locations in a sparse manner.
+In order to find out the similarity between two locations, we propose a straightforward function that contains the detection confidences of the image and the landmark coordinates in 3D.
+Recognition of the previously visited and unvisited locations are also considered in the framework.
+Examplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a depth camera (Kinect) mounted differential drive autonomous ground vehicle.
+The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known simultaneously localization and mapping(SLAM) problem.
+The algorithm is tested in three different datasets of different lighting conditions.
 Additional depth information beside the actual image increases the detection rate especially in dark.

### 2014-12-01 latex-spie/article.tex
Speed performance is almost finished.

--- 2014-12-01 latex-spie/article.tex
@@
 After that, the difference matrices are calculated to examine the results.
-Nearest Neighbour (NN) algorithm is utilized to classify the new locations and the distance metric is $L_{1}$.
+Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
+In addition to this, the last 100 sequential frames are not involved in classification phase, because it is assumed that the sensor is always moving and these frames correspond to the just behind of the sensor.
 
 The method described in Section \ref{sec:method} has basically two parameters that must be adjusted.
-One of them is $k\times k$ the size of subimages that the input image partitioned by in (\ref{eq:divided_mat}) and the other one is $n$ the order of the Zernike polynomials.
-During the experiments, the parameter set is selected as $k=30$ and $n=2$.
-Then the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions.
+One of them is $k\times k$ which defines the number of the subimages that the input image was partitioned to, and the other one is n, which is the order of the Zernike polynomials used.
+During the experiments, the selected parameters are $k = 30$ and $n = 2$.
+Then, the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions.
 The histograms of each subregion are simply concatenated to compose the feature vector of an image.
-In order to construct the ultimate feature vector containing both gray and depth images, each feature vectors obtained from both images are also concatenated.
+In order to construct the ultimate feature vector containing both gray and depth images, each feature vector obtained from both images are also concatenated.
 
@@
 
-In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in an indoor environment by using Kinect sensor which can grab both RGB and depth images at the same time.
-The lighting conditions in the datasets are bright, dim and dark in which both depth and RGB images are captured.
+In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in an indoor environment by using Kinect sensor which can grab both gray and depth images at the same time.
+The lighting conditions in the datasets are bright, dim and dark in which both depth and gray images are captured.
 The exemplary images belonging to different datasets are shown in Figure \ref{fig:dataset}.
@@
 
+Ama sunu muhakkak eklemen gerek; el ile secilen bir maskeye dayanarak sonuc hesapliyorsun dolayisiyla sonuclarda hatalar olabilir.
+(ornek: the performance shown in Table/figure is  representative as the results are obtained with a manually annotated É.).
+Daha sonra da goz ile saydigin FP/FN sayilarini verirsin, ki bu sayiyi ben de merak ediyorum.
+En sonda da asil basarimin video uzerinden degerlendirilecegini yazarsin.
+(ornek: our demo video provides qualitative loop closure results which may be considered to be more representative for our methodÕs performance).
+
 \subsection{Detection Performance}
@@
 \subsection{Real-Time Performance}
+
+Most of image-to-image loop closure techniques are void of computational efficient.
+There exist limited number of techniques that operates in real-time without parallelization.
+The speed tests are done with a MacBook Pro 7,1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
+In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
+The NN classification is applied with simple brute-force searching in which the algorithmic complexty is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
+In other words, the amount of time needed to performs this search increases throughout the trajectory.
+Therefore, the total processing time including the brute force search is $14ms$ in average.
 

### 2014-12-01 latex-spie/article.tex
Abstract and Real-Time performance is finished

--- 2014-12-01 latex-spie/article.tex
@@
 \begin{abstract}
-Visual loop closure detection problem is an active area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
-In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction with saliency detection technique.
-In contradistinction to the previous methods, our approach uses additional depth information.
-Saliency regions are used to refer to the certain distinctive areas on the image patches.
-They are also suitable to represent locations in a sparse manner.
-In order to find out the similarity between two locations we use a straightforward function, that contains the detection confidences of the image and the landmark coordinates in 3D.
-Recognition of the previously visited and unvisited locations is also considered in the framework.
-Exemplary results and the practical implementation of the method are also given with the data gathered on the testbed with a depth camera (Kinect) mounted differential drive autonomous ground vehicle.
-Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location.
-The algorithm is tested in three different datasets which lighting conditions are different from each other.
+In this paper, we present an enhanced loop closure method based on image-to-image matching  relies on Quantized Local Zernike Moments.
+In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike Moments in local manner.
+These moments are used to represent holistic shape information inside the image.
+The complex moments that are extracted from both gray and depth images are coarsely quantized.
+In order to find out the similarity between two locations, Nearest Neighbour classification algorithm is performed.
+Examplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect.
+The method is evaluated in three different datasets of different lighting conditions.
 Additional depth information beside the actual image increases the detection rate especially in dark.
+The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known Simultaneously Localization and mapping (SLAM) problem.
+This technique is quite simple because of its low computational complexity, and performs in real-time with high loop closing accuracy.
+
 \end{abstract}
 
-\keywords{Loop closure, depth map, zernike moments,  computer vision}
+\keywords{Loop closure, Zernike Moments, image processing, SLAM, depth map, indoor navigation}
 
@@
 In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors.
-One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM) which still remains as an assertive problem in a lot of ways.
+One of the major problems linked to robotic navigation is SLAM which still remains as an assertive problem in a lot of ways.
 Loop closing is defined as the correct identification of previously visited location in terms of SLAM.
@@
 Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
-In addition to this, the last 100 sequential frames are not involved in classification phase, because it is assumed that the sensor is always moving and these frames correspond to the just behind of the sensor.
+In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.
 
@@
 
+As it can be seen in Figure \ref{subfig:pr_bright}
+
 \subsection{Real-Time Performance}
 
-Most of image-to-image loop closure techniques are void of computational efficient.
-There exist limited number of techniques that operates in real-time without parallelization.
+There exist limited number of techniques that operate in real-time without parallelization.
 The speed tests are done with a MacBook Pro 7,1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
 In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
-The NN classification is applied with simple brute-force searching in which the algorithmic complexty is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
+The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
 In other words, the amount of time needed to performs this search increases throughout the trajectory.
-Therefore, the total processing time including the brute force search is $14ms$ in average.
+Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.
 

### 2014-12-01 latex-spie/article.tex
last sentence of abstract

@@
 \begin{abstract}
-In this paper, we present an enhanced loop closure method based on image-to-image matching  relies on Quantized Local Zernike Moments.
-In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike Moments in local manner.
+In this paper, we present an enhanced loop closure method based on image-to-image matching  relies on quantized local Zernike moments.
+In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike moments in local manner.
 These moments are used to represent holistic shape information inside the image.
-The complex moments that are extracted from both gray and depth images are coarsely quantized.
-In order to find out the similarity between two locations, Nearest Neighbour classification algorithm is performed.
-Examplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect.
+The moments in complex space that are extracted from both grayscale and depth images are coarsely quantized.
+In order to find out the similarity between two locations, nearest neighbour (NN) classification algorithm is performed.
+Exemplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect.
 The method is evaluated in three different datasets of different lighting conditions.
-Additional depth information beside the actual image increases the detection rate especially in dark.
-The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known Simultaneously Localization and mapping (SLAM) problem.
-This technique is quite simple because of its low computational complexity, and performs in real-time with high loop closing accuracy.
+Additional depth information with the actual image increases the detection rate especially in dark enviroments.
+The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known simultaneously localization and mapping (SLAM) problem.
+This technique is applicable because of its low computational complexity, and performs in real-time with high loop closing accuracy.
 
@@
 
-\keywords{Loop closure, Zernike Moments, image processing, SLAM, depth map, indoor navigation}
+\keywords{Loop closure, Zernike moments, image processing, SLAM, depth map, indoor navigation}
 

### 2014-12-01 latex-spie/article.tex
minor typho changes

@@
 The method is evaluated in three different datasets of different lighting conditions.
-Additional depth information with the actual image increases the detection rate especially in dark enviroments.
+Additional depth information with the actual image increases the detection rate especially in dark environments.
 The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known simultaneously localization and mapping (SLAM) problem.
-This technique is applicable because of its low computational complexity, and performs in real-time with high loop closing accuracy.
+This technique is also practically applicable because of its low computational complexity, and performing capability in real-time with high loop closing accuracy.
 
@@
 These moments are used to represent shape information inside the image within the context of image processing.
-To make the image description more robust, the ZMs of the input image is calculated in local manner.
-In this study, the ZMs are extracted from both the greyscale and depth images separately and concatenated sequentially to create ultimate feature vector.
+To make the image description more robust, the CZMs of the input image is calculated in local manner.
+In this study, the CZMs are extracted from both the greyscale and depth images separately and concatenated sequentially to create ultimate feature vector.
 
@@
 The whole image representation is constructed as follows.
-Firstly, the ZMs of each subimage that were obtained by partitioning the input image is calculated.
+Firstly, the CZMs of each subimage that were obtained by partitioning the input image is calculated.
 After that, the calculated complex moments are coarsely quantized by keeping only the sign of the real and imaginary components and ignoring the rest of the information.
@@
 
-The Complex Zernike Moments (ZM) of an image are used to represent the image on the 2-dimensional complex subspace.
+The CZMs of an image are used to represent the image on the 2-dimensional complex subspace.
 They are extracted using a set of complex polynomials which form a complete orthogonal radial basis functions defined on the unit disc.
@@
 
-The Complex Zernike Moments of an image $f(i,j)$ are calculated as follows:
+The CZMs of an image $f(i,j)$ are calculated as follows:
 
@@
 
-In order to extract ZMs in local manner, the input image is divided by $k\times k$-sized subimages in which $k$ is a predefined partitioning parameter.
+In order to extract CZMs in local manner, the input image is divided by $k\times k$-sized subimages in which $k$ is a predefined partitioning parameter.
 If the image is not divided by $k$ perfectly, the rest of the part is simply ignored.
@@
 After that, the difference matrices are calculated to examine the results.
-Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
+The NN algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
 In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.
@@
 
-\subsection{Benchmark Datasets}
+\subsection{Benchmark of the Datasets}
 
@@
 There exist limited number of techniques that operate in real-time without parallelization.
-The speed tests are done with a MacBook Pro 7,1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
+The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
 In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
-The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
+The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(n)$ that depends on the number of frames to compare with.
 In other words, the amount of time needed to performs this search increases throughout the trajectory.

### 2014-12-01 latex-spie/article.tex
Figures are changed with grayscale versions

--- 2014-12-01 latex-spie/article.tex
@@
 Evangelos Sariyanidi\supit{b}, 
-Onur Sencan\supit{c}, 
-Hakan Temeltas\supit{c}
+Onur Sencan\supit{a}, 
+Hakan Temeltas\supit{a}
 \skiplinehalf
-\supit{a}Istanbul Technical University Mechatronics Engineering Department, Maslak 34469, Istanbul, Turkey; 
-\supit{b}Centre of Intelligent Sensing, Mile End Road, E1 4NS, London, U.K.;
-\supit{c}Istanbul Technical University Control and Automation Engineering Department, Maslak 34469, Istanbul, Turkey
+\supit{a}Istanbul Technical University Control and Automation Engineering Department, \\
+Maslak 34469, Istanbul, Turkey; \\
+\supit{b}Centre of Intelligent Sensing, Mile End Road, E1 4NS, London, U.K.
 }

### 2014-12-01 latex-spie/article.tex
Results...

@@
 
-Ama sunu muhakkak eklemen gerek; el ile secilen bir maskeye dayanarak sonuc hesapliyorsun dolayisiyla sonuclarda hatalar olabilir.
-(ornek: the performance shown in Table/figure is  representative as the results are obtained with a manually annotated É.).
-Daha sonra da goz ile saydigin FP/FN sayilarini verirsin, ki bu sayiyi ben de merak ediyorum.
-En sonda da asil basarimin video uzerinden degerlendirilecegini yazarsin.
-(ornek: our demo video provides qualitative loop closure results which may be considered to be more representative for our methodÕs performance).
+The results are obtained by three datasets in which the trajectory of the Kinect mounted moving platform is similar to each Dataset that is created in different lightning conditions: Bright, Dim and Dark.
+In the first loop, there are no loop closures to detect.
+To examine the performance of the method, precision vs.
+recall (PR) curves are calculated for each dataset.
+Precision is simply the fraction of retrieved instances that are relevant, while recall is the fraction of relevant instances that are retrieved.
+In other words, there are less false positives when the precision is high, and less false negatives when the recall is high.
+In loop closing problem, high precision is needed to decrease localization errors of the moving autonomous vehicle.
+The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image source that are only graysalce images, only depth images and both.
+The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.....
+
+%VANGELden
+%the performance shown in Table/figure is  representative as the results are obtained with a %manually annotated É.
+%our demo video provides qualitative loop closure results which may be considered to be more representative for our methodÕs performance
 
@@
 
-\subsection{Real-Time Performance}
+\subsection{Online Performance}
 
@@
         \caption{Dark dataset results.}
-        \label{subfig:pr_bright}
+        \label{subfig:pr_dark}
         \end{subfigure}
@@
         \caption{Comparison between datasets.}
-        \label{subfig:pr_dim}
+        \label{subfig:pr_all}
         \end{subfigure}

### 2014-12-01 latex-spie/article.tex
changes in captions

@@
         \vspace{3mm}
-        \caption{Image partitioned into blocks by k = 3}
+        \caption{Image partitioned into $3\times 3$ blocks ($k = 3$).}
         \label{fig:divided_image}
@@
         \hspace{-3mm}
-        \caption{Examplary images belonging to benchmark datasets in different lighting conditions.}
+        \caption{Examplary images belonging to benchmark datasets in three different lighting conditions.}
         \label{fig:dataset}
@@
 In loop closing problem, high precision is needed to decrease localization errors of the moving autonomous vehicle.
-The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image source that are only graysalce images, only depth images and both.
-The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.....
+The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image source that are only grayscale images, only depth images and both.
+The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.
 
@@
 There exist limited number of techniques that operate in real-time without parallelization.
-The speed tests are done with a MacBook Pro 7,1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
+The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
 In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
@@
         \hspace{-3mm}
-        \caption{Distance matrixes}
+        \caption{Similarity matrices of the captured images in experimental results.
+Condensed fray shades point out to positive alikeness between scenes.
+The black lines in lower triangle indicates user specified ground truths.
+The gray lines in upper-triangle shows the obtained results.}
         \label{fig:dist_matrices}

### 2014-12-01 latex-spie/article.tex
minor text
asdasdsad

@@
 %VANGELden
-%the performance shown in Table/figure is  representative as the results are obtained with a %manually annotated É.
-%our demo video provides qualitative loop closure results which may be considered to be more representative for our methodÕs performance
+%the performance shown in Table/figure is  representative as the results are obtained with a %manually annotated ….
+%our demo video provides qualitative loop closure results which may be considered to be more representative for our method’s performance
 
@@
         \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dist_bright.png}    
-        \caption{Bright distances}
+        \caption{Bright}
         \label{subfig:dist_bright}
@@
         \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dist_dim.png}    
-        \caption{Dim distances}
+        \caption{Dim}
         \label{subfig:dist_dim}
@@
         \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/dist_dark.png}    
-        \caption{Dark distances}
+        \caption{Dark}
         \label{subfig:dist_dark}
@@
         \caption{Similarity matrices of the captured images in experimental results.
-Condensed fray shades point out to positive alikeness between scenes.
-The black lines in lower triangle indicates user specified ground truths.
-The gray lines in upper-triangle shows the obtained results.}
+Condensed gray shades point out to positive alikeness between scenes.
+The black dots in lower triangle indicates detected loop closures at $90\%$ precision.}
         \label{fig:dist_matrices}
@@
 \end{document}
-
-%----------------------------------------------------------------------------------------------------
-% % % % % % % % % % % % % % % % % % % % % % % % COMMENTED 
-%----------------------------------------------------------------------------------------------------
-
-\begin{comment}
-
-This document shows the desired format and appearance of a manuscript prepared for the Proceedings of the SPIE.\footnote{The basic format was developed in 1995 by Rick Herman (SPIE) and Ken Hanson (Los Alamos National Lab.).} It is prepared using LaTeX2e\cite{Lamport94} with the class file {\tt spie.cls}.
-The LaTeX source file used to create this document is {\tt article.tex}, which contains important formatting information embedded in it.
-These files are available on the Internet at {\tt http://home.lanl.gov/kmh/spie/}.
-The font used throughout is the LaTeX default font, Computer Modern Roman, which is equivalent to the Times Roman font available on many systems.
-If this font is not available, use a similar serif font.
-Normal text has a font size of 10 points\footnote{Font sizes are specified in points, abbreviated pt., which is a unit of length.
-One inch = 72.27 pt.; one cm = 28.4 pt.} for which the actual height of a capital E is about 2.4 mm (7 pt.) and the line-to-line spacing is about 4.2 mm (12 pt.).
-The font attributes for other parts of the manuscript, summarized in Table~\ref{tab:fonts}, are described in the following sections.
-Normal text should be justified to both the left and right margins.
-Appendix~\ref{sec:latex} has information about PostScript fonts.
-
-To be properly reproduced in the Proceedings, all text and figures must fit inside a rectangle 6.75-in.\ wide by 8.75-in.\ high or 17.15 cm by 22.23 cm.
-The text width and height are set in {\tt spie.cls} to match this requirement.
-%% This table is carefully placed in the source file to make 
-%% it appear at bottom of page, but above the footnotes.  
-%% Use of [h] in following command forces table to appear "here".
-\begin{table}[h]
-\caption{Fonts sizes to be used for various parts of the manuscript.
-All fonts are Computer Modern Roman or an equivalent.
-Table captions should be centered above the table.
-When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.}
-\label{tab:fonts}
-\begin{center}       
-\begin{tabular}{|l|l|} %% this creates two columns
-%% |l|l| to left justify each column entry
-%% |c|c| to center each column entry
-%% use of \rule[]{}{} below opens up each row
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, centered  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author names and affiliations & 12 pt., normal, centered   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Section heading & 11 pt., bold, centered (all caps)  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 11 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 10 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Normal text & 10 pt., normal  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Figure and table captions & \, 9 pt., normal \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Footnote & \, 9 pt., normal \\
-\hline 
-\end{tabular}
-\end{center}
-\end{table} 
-The text should begin 1.00 in.\ or 2.54 cm from the top of the page.
-The right and left margins should be 0.875~in.\ or 2.22 cm for US letter-size paper (8.5 in.\ by 11 in.) or 1.925 cm for A4 paper (210 mm by 297 mm) to horizontally center the text on the page.
-See Appendix~\ref{sec:latex} for guidance regarding paper-size specification.
-
-Authors are encouraged to follow the principles of sound technical writing, as described in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
-Many aspects of technical writing are addressed in the {\em AIP Style Manual}, published by the American Institute of Physics.
-It is available on line at {\tt http://www.aip.org/pubservs/style/4thed/toc.html} or {\tt http://public.lanl.gov/kmh/AIP\verb+_+Style\verb+_+4thed.pdf}.
-A spelling checker is helpful for finding misspelled words.
-
-An author may use this LaTeX source file as a template by substituting his/her own text in each field.
-This document is not meant to be a complete guide on how to use LaTeX.
-For that, refer to books on LaTeX usage, such as the definitive work by Lamport\cite{Lamport94} or the very useful compendium by Mittelbach et al.\cite{Mittelbach04}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{PARTS OF MANUSCRIPT}
-
-This section describes the normal structure of a manuscript and how each part should be handled.
-The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.
-In LaTeX, paragraphs are separated by blank lines in the source file.
-
-At times it may be desired, for formatting reasons, to break a line without starting a new paragraph.
-This situation may occur, for example, when formatting the article title, author information, or section headings.
-Line breaks are inserted in LaTeX by entering \verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired location.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SECTION FORMATTING} \label{sec:sections}
-
-Section headings are centered and formatted completely in uppercase 11-point bold font.
-Sections should be numbered sequentially, starting with the first section after the Abstract.
-The heading starts with the section number, followed by a period.
-In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.
-
-Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style\cite{Lamport94}.
-The same goes for leading paragraphs of subsections and sub-subsections.
-Subsequent paragraphs are standard paragraphs, with 14-pt.\ (5 mm) indentation.
-An extra half-line space should be inserted between paragraphs.
-In LaTeX, this spacing is specified by the parameter \verb|\parskip|, which is set in {\tt spie.cls}.
-Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.
-
-%%-----------------------------------------------------------
-\subsection{Subsection Attributes}
-
-The subsection heading is left justified and set in 11-point, bold font.
-Capitalization rules are the same as those for book titles.
-The first word of a subsection heading is capitalized.
-The remaining words are also capitalized, except for minor words with fewer than four letters, such as articles (a, an, and the), short prepositions (of, at, by, for, in, etc.), and short conjunctions (and, or, as, but, etc.).
-Subsection numbers consist of the section number, followed by a period, and the subsection number within that section.
-
-%%-----------
-\subsubsection{Sub-subsection attributes} 
-The sub-subsection heading is left justified and its font is 10 point, bold.
-Capitalize as for sentences.
-The first word of a sub-subsection heading is capitalized.
-The rest of the heading is not capitalized, except for acronyms and proper names.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{FIGURES AND TABLES}
-
-Figures are numbered in the order of their first citation.
-They should appear in numerical order and on or after the same page as their first reference in the text.
-Alternatively, all figures may be placed at the end of the manuscript, that is, after the Reference section.
-It is preferable to have figures appear at the top or bottom of the page.
-Figures, along with their captions, should be separated from the main text by at least 0.2 in.\ or 5 mm.
-
-Figure captions are centered below the figure or graph.
-Figure captions start with the figure number in 9-point bold font, followed by a period; the text is in 9-point normal font; for example, ``{\footnotesize{Figure 3.}  Original image...}".
-See Fig.~\ref{fig:example} for an example of a figure caption.
-When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.
-
-Tables are handled identically to figures, except that their captions appear above the table. 
-%%  Use following command to specify that graphics file is in 
-%%  a directory other than this LaTeX source file.
-%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
-%%\graphicspath{{H:/HANSON/SPIESTY/}}
-%% tabular environment useful for creating an array of images  
-%-------------
-   \begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[height=7cm]{figures/mcr3b.eps}
-   \end{tabular}
-   \end{center}
-   \caption[example] 
-%>>>> use \label inside caption to get Fig. number with \ref{}
-   { \label{fig:example} 
-Figure captions are used to describe the figure and help the reader understand it's significance.
-The caption should be centered underneath the figure and set in 9-point font.
-It is preferable for figures and tables to be placed at the top or bottom of the page.
-LaTeX tends to adhere to this standard.}
-   \end{figure} 
-%-------------
-
-For further details concerning the inclusion of grayscale and color images, consult SPIE's {\it Author Guide for Publication and Presentation}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix    %>>>> this command starts appendixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{MISCELLANEOUS FORMATTING DETAILS} \label{sec:misc}
-
-It is often useful to refer back (or forward) to other sections in the article.
-Such references are made by section number.
-When a section reference starts a sentence, Section is spelled out; otherwise use its abbreviation, for example, ``In Sec.~2 we showed..." or ``Section~2.1 contained a description...".
-References to figures, tables, and theorems are handled the same way.
-
-At the first occurrence of an acronym, spell it out, followed by the acronym in parentheses, e.g., noise power spectrum (NPS).
-
-%%-----------------------------------------------
-\subsection{Formatting Equations} 
-Equations may appear in line with the text, if they are simple, short, and not of major importance; e.g., $\beta = b/r$.
-Important equations appear on their own line.
-Such equations are centered.
-For example, ``The expression for the minus-log-posterior is
-	\begin{equation}
-	\label{eq:alpha}
-\phi = |{\rm\bf y} - {\rm\bf A}{\rm\bf x}|^2 + \alpha \log p({\rm\bf x}) \, ,
-	\end{equation}
-where $\alpha$ determines the strength of ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.
-
-Equations are considered to be part of a sentence and should be punctuated accordingly.
-In the above example, a comma follows the equation because the next line is a subordinate clause.
-If the equation ends the sentence, a period should follow the equation.
-The line following an equation should not be indented unless it is meant to start a new paragraph.
-Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.
-
-References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:alpha}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..."  Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks.
-
-%%-----------------------------------------------------------
-\subsection{Formatting Theorems}
-
-To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified and followed by a period.
-The text of the theorem continues on the same line in normal, 10-point font.
-For example,
-
-\noindent{\bf Theorem 1.} For any unbiased estimator...
-
-Formal statements of lemmas and algorithms receive a similar treatment.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SOME LATEX GUIDANCE} \label{sec:latex}
-
-%%-----------------------------------------------------------
-\subsection{Margins and PostScript Fonts}
-
-Manuscripts submitted electronically to as PostScript (PS) files must have the correct margins.
-LaTeX margins are related to the document's paper size.
-The paper size is set at two separate places in the process of creating a PS file.
-The first place is in {\tt latex}.
-The default in {\tt article.tex}, on which {\tt spie.cls} is based, is USA letter paper.
-To format a document for A4 paper, the first line of the LaTeX source file should be \verb|\documentclass[a4paper]{spie}|.
-
-The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.
-The application DVIPS is typically used to convert the DVI file to a PS file.
-DVIPS has its own default paper size, which can be overridden with the option ``{\tt -t letter}" or ``{\tt -t a4}".
-If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command, for example.
-
-Another DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file.
-This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.
-The option ``{\tt -P pdf}" makes DVIPS include these fonts in its output PS file.
-
-%%-----------------------------------------------------------
-\subsection{Bold Math Symbols}
-
-The math package from the American Mathematical Society allows one to easily produce bold math symbols, well beyond what is available in LaTeX.
-It also provides many useful capabilities for creating elaborate mathematical expressions.
-You need to load the AMS math package near the top of the LaTeX source file, right after the \verb+\documentclass+ command:\\[1ex]
-\verb+\usepackage[]{amsmath}+ \\[1ex]
-Then for bold math symbols use \verb+\boldsymbol+ in equations, e.g., 
-\verb+$\boldsymbol{\pi}$+ 
-yields a bold pi.  You can make it easier to use by defining a command:\\[1ex]
-\verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
-and then using it like so \verb+$\bm{\pi}$+.
-
-Not all math symbols are available in bold.
-In a pinch, you can use \verb+\pmb+ ("poor man's bold"), which is defined in \verb+amsmath+.
-This command approximates a bold character with a superposition of several, slightly displaced unbold characters.
-
-If you want a Greek symbol in the article title, it should be both larger and bold. The easiest thing is to load the AMS math package as described above. 
-Then, in the title, use something like:\\[1ex]
-\verb+\title{Estimation of {\LARGE$\boldsymbol\alpha$} by a Monte Carlo technique}+ \\[1ex]
-Note that the command to create the alpha character is enclosed within braces to form a self-contained environment.
-The use of \verb+\LARGE+ in this example may not be needed when using nondefault font packages, such as the {\tt times} package, because of how the article title is handled in {\tt spie.cls}.
-
-%%-----------------------------------------------------------
-\subsection{Uppercase letters and special symbols in BibTex}
-
-BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case.
-BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.
-
-The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged in braces.
-Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
-\verb+ @article{Kaczmarz37,+ \\ 
-\verb+ author = "S. Kaczmarz",+ \\ 
-\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen linearer {G}leichungen",+ \\ 
-\verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
-\verb+ volume = "A35",+ \\ 
-\verb+ pages  = "355-357",+ \\	
-\verb+ year   = "1937"	} + \\[1ex]
-This example shows the use of both umlauts and uppercase letters.
-
-\end{comment}

### 2014-12-01 latex-spie/article.tex
conclusion is added
captions are updated

--- 2014-12-01 latex-spie/article.tex
@@
 
-\subsection{Online Performance}
-
-There exist limited number of techniques that operate in real-time without parallelization.
-The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
-In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
-The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
-In other words, the amount of time needed to performs this search increases throughout the trajectory.
-Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.
-
 % DISTANCE MATRICES
-\begin{figure}[!htb]
+\begin{figure}
         \centering
@@
 
+\subsection{Online Performance}
+
+There exist limited number of techniques that operate in real-time without parallelization.
+The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
+In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
+The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
+In other words, the amount of time needed to performs this search increases throughout the trajectory.
+Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.
+
 % RESULTS
-\begin{figure}[!htb]
+\begin{figure}
         \centering
@@
         \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
-        \caption{Bright dataset results.}
+        \caption{Bright}
         \label{subfig:pr_bright}
@@
         \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
-        \caption{Dim dataset results.}
+        \caption{Dim}
         \label{subfig:pr_dim}
@@
         \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
-        \caption{Dark dataset results.}
+        \caption{Dark}
         \label{subfig:pr_dark}
@@
         \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
-        \caption{Comparison between datasets.}
+        \caption{Comparison between datasets when both grayscale and depth images are utilized.}
         \label{subfig:pr_all}
@@
         \hspace{-3mm}
-        \caption{PR curves}
+        \caption{Precision vs. Recall curves of the results.}
         \label{fig:pr_curves}
@@
 %----------------------------------------------------------------------------------------------------
-% CONCLUSION AND FUTURE WORK
+% CONCLUSION
 %----------------------------------------------------------------------------------------------------
 
-\section{CONCLUSION AND FUTURE WORK}
+\section{CONCLUSION}
+
+In conclusion, this paper presents a novel image description technique that is used to achieve loop closure detection within a SLAM framework.
+The technique works quite rapidly and operates in real-time.
+Moreover, it results successful loop closing on different lightning conditions by using the depth information.
 

### 2014-12-01 latex-spie/article.tex
added ACKNOWLEDGEMENTS

@@
 To examine the performance of the method, precision vs.
-recall (PR) curves are calculated for each dataset.
-Precision is simply the fraction of retrieved instances that are relevant, while recall is the fraction of relevant instances that are retrieved.
-In other words, there are less false positives when the precision is high, and less false negatives when the recall is high.
-In loop closing problem, high precision is needed to decrease localization errors of the moving autonomous vehicle.
-The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image source that are only grayscale images, only depth images and both.
+recall (PR) curves are plotted for each dataset.
+The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image sources that are only grayscale images, only depth images and both.
 The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.
+In addition to this, the similarity matrices calculated from each dataset is shown in \ref{fig:dist_matrices}.
+The black dots corresponds to the detected loop closures at $90\%$ precision.
+As it can be seen in the similarity matrices, the algorithm performs quite successful results to detect loop closure event.
 
@@
 %our demo video provides qualitative loop closure results which may be considered to be more representative for our method’s performance
-
-\subsection{Detection Performance}
-
-As it can be seen in Figure \ref{subfig:pr_bright}
 
@@
 
-In conclusion, this paper presents a novel image description technique that is used to achieve loop closure detection within a SLAM framework.
+In conclusion, this paper presents a novel image description technique\footnote{Readers can access the source code from the following link: \emph{https://github.com/ituroboticslab/Quantized-Local-Zernike-Moments}} that is used to achieve loop closure detection within a SLAM framework.
 The technique works quite rapidly and operates in real-time.
@@
 
+Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory and the Borda Technology for the indoor dataset retrieval.
+
 %----------------------------------------------------------------------------------------------------

### 2014-12-01 latex-spie/article.tex
almost finished

@@
 \begin{abstract}
-In this paper, we present an enhanced loop closure method based on image-to-image matching  relies on Quantized Local Zernike Moments.
+In this paper, we present an enhanced loop closure method\footnote{Readers can access the source code from the following link: \\https://github.com/ituroboticslab/Quantized-Local-Zernike-Moments} based on image-to-image matching  relies on Quantized Local Zernike Moments.
 In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike Moments in local manner.
@@
 
-\subsection{Benchmark of the Datasets}
+\subsection{Datasets}
 
@@
 
-        \hspace{-3mm}
+        \hspace{-2mm}
         \caption{Examplary images belonging to benchmark datasets in three different lighting conditions.}
@@
 In the first loop, there are no loop closures to detect.
-To examine the performance of the method, precision vs.
-recall (PR) curves are plotted for each dataset.
+To examine the performance of the method, precision-recall (PR) curves are plotted for each dataset.
 The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image sources that are only grayscale images, only depth images and both.
@@
 %our demo video provides qualitative loop closure results which may be considered to be more representative for our method’s performance
+
+\subsection{Online Performance}
+
+There exist limited number of techniques that operate in real-time without parallelization.
+The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
+In this setting, the extraction of Quantized local Zernike moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
+The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
+In other words, the amount of time needed to performs this search increases throughout the trajectory.
+Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.
 
@@
 
-        \hspace{-3mm}
+        \hspace{-2mm}
         \caption{Similarity matrices of the captured images in experimental results.
@@
 \end{figure}
-
-\subsection{Online Performance}
-
-There exist limited number of techniques that operate in real-time without parallelization.
-The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
-In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
-The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
-In other words, the amount of time needed to performs this search increases throughout the trajectory.
-Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.
 
@@
         \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
-        \caption{Comparison between datasets when both grayscale and depth images are utilized.}
+        \caption{Comparison between the datasets.}
         \label{subfig:pr_all}
@@
         \hspace{-3mm}
-        \caption{Precision vs. Recall curves of the results.}
+        \caption{The precision-recall curves of our method.}
         \label{fig:pr_curves}
@@
 
-In conclusion, this paper presents a novel image description technique\footnote{Readers can access the source code from the following link: \emph{https://github.com/ituroboticslab/Quantized-Local-Zernike-Moments}} that is used to achieve loop closure detection within a SLAM framework.
+In conclusion, this paper presents a novel image description technique that is used to achieve loop closure detection within a SLAM framework.
 The technique works quite rapidly and operates in real-time.

### 2014-12-01 latex-spie/article.tex
almost finished

@@
 
-%----------------------------------------------------------------------------------------------------
-% EXPERIMENTS
-%----------------------------------------------------------------------------------------------------
-
-\section{EXPERIMENTS}
-
-The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other.
-The tests are done with either using gray and depth images separately or using both of them.
-After that, the difference matrices are calculated to examine the results.
-Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
-In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.
-
-The method described in Section \ref{sec:method} has basically two parameters that must be adjusted.
-One of them is $k\times k$ which defines the number of the subimages that the input image was partitioned to, and the other one is n, which is the order of the Zernike polynomials used.
-During the experiments, the selected parameters are $k = 30$ and $n = 2$.
-Then, the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions.
-The histograms of each subregion are simply concatenated to compose the feature vector of an image.
-In order to construct the ultimate feature vector containing both gray and depth images, each feature vector obtained from both images are also concatenated.
-
-\subsection{Datasets}
-
-In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in an indoor environment by using Kinect sensor which can grab both gray and depth images at the same time.
-The lighting conditions in the datasets are bright, dim and dark in which both depth and gray images are captured.
-The exemplary images belonging to different datasets are shown in Figure \ref{fig:dataset}.
-In some cases, the line of sight of the Kinect is not enough to capture the depth information for distances above $10m$.
-Thus, some of the depth images are unreliable.
-
-The images in the datasets are acquired via Kinect mounted moving platform and pointed in the direction of the displacement with approximate speed 0.25m/s.
-Also, the rectangle-shaped trajectory of the three datasets is almost the same as the others to compare their performances correctly.
-There are two loops that contain around 1000 frames per loop in each dataset, first one is used for discovering and the second for evaluating.
-To create the ground truth, the locations which corresponds to approximately 10 sequential frames are annotated manually.
-
 % BENCHMARK DATASETS
-\begin{figure}[!htb]
+\begin{figure}
         \centering
@@
 \end{figure}
+
+%----------------------------------------------------------------------------------------------------
+% EXPERIMENTS
+%----------------------------------------------------------------------------------------------------
+
+\section{EXPERIMENTS}
+
+The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other.
+The tests are done with either using grayscale and depth images separately or using both of them.
+After that, the difference matrices are calculated to examine the results.
+Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
+In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.
+
+The method described in Section \ref{sec:method} has basically two parameters that must be adjusted.
+One of them is $k\times k$ which defines the number of the subimages that the input image was partitioned to, and the other one is n, which is the order of the Zernike polynomials used.
+During the experiments, the selected parameters are $k = 30$ and $n = 2$.
+Then, the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions.
+The histograms of each subregion are simply concatenated to compose the feature vector of an image.
+In order to construct the ultimate feature vector containing both grayscale and depth images, each feature vector obtained from both images are also concatenated.
+
+% RESULTS
+\begin{figure}
+        \centering
+
+        %%% BRIGHT PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
+        \caption{Bright}
+        \label{subfig:pr_bright}
+        \end{subfigure}
+        ~ 
+        %%% DIM PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
+        \caption{Dim}
+        \label{subfig:pr_dim}
+        \end{subfigure}
+        ~
+        %%% DARK PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
+        \caption{Dark}
+        \label{subfig:pr_dark}
+        \end{subfigure}
+        ~ 
+        %%% ALL PR CURVE
+        \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
+        \caption{Comparison between the datasets.}
+        \label{subfig:pr_all}
+        \end{subfigure}
+
+        \hspace{-3mm}
+        \caption{The precision-recall curves of our method.}
+        \label{fig:pr_curves}
+\end{figure}
+
+\subsection{Datasets}
+
+In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in an indoor environment by using Kinect sensor which can grab both grayscale and depth images at the same time.
+The lighting conditions in the datasets are bright, dim and dark in which both depth and grayscale images are captured.
+The exemplary images belonging to different datasets are shown in Figure \ref{fig:dataset}.
+In some cases, the line of sight of the Kinect is not enough to capture the depth information for distances above $10m$.
+Thus, some of the depth images are unreliable.
+
+The images in the datasets are acquired via Kinect mounted moving platform and pointed in the direction of the displacement with approximate speed 0.25m/s.
+Also, the rectangle-shaped trajectory of the three datasets is almost the same as the others to compare their performances correctly.
+There are two loops that contain around 1000 frames per loop in each dataset, first one is used for discovering and the second for evaluating.
+To create the ground truth, the locations which corresponds to approximately 10 sequential frames are annotated manually.
 
@@
 
-% RESULTS
-\begin{figure}
-        \centering
-
-        %%% BRIGHT PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-         % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
-        \caption{Bright}
-        \label{subfig:pr_bright}
-        \end{subfigure}
-        ~ 
-        %%% DIM PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-         % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
-        \caption{Dim}
-        \label{subfig:pr_dim}
-        \end{subfigure}
-        ~
-        %%% DARK PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-         % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
-        \caption{Dark}
-        \label{subfig:pr_dark}
-        \end{subfigure}
-        ~ 
-        %%% ALL PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-         % trim parameters by order: left, bottom, right, top
-        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
-        \caption{Comparison between the datasets.}
-        \label{subfig:pr_all}
-        \end{subfigure}
-
-        \hspace{-3mm}
-        \caption{The precision-recall curves of our method.}
-        \label{fig:pr_curves}
-\end{figure}
-
 %----------------------------------------------------------------------------------------------------

### 2014-12-01 latex-spie/article.tex
almost finished

@@
 
-Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory and the Borda Technology for the indoor dataset retrieval.
+Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory, and Borda Technology for the indoor dataset retrieval.
 

### 2014-12-02 latex-spie/article.tex
almost finished

@@
 \begin{abstract}
-In this paper, we present an enhanced loop closure method\footnote{Readers can access the source code from the following link: \\https://github.com/ituroboticslab/Quantized-Local-Zernike-Moments} based on image-to-image matching  relies on Quantized Local Zernike Moments.
-In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike Moments in local manner.
+In this paper, we present an enhanced loop closure method\footnote{Readers can access the source code from the following link: \\https://github.com/ituroboticslab/Quantized-Local-Zernike-Moments} based on image-to-image matching  relies on quantized local Zernike moments.
+In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike moments in local manner.
 These moments are used to represent holistic shape information inside the image.
-The complex moments that are extracted from both gray and depth images are coarsely quantized.
-In order to find out the similarity between two locations, Nearest Neighbour classification algorithm is performed.
-Examplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect.
+The moments in complex space that are extracted from both grayscale and depth images are coarsely quantized.
+In order to find out the similarity between two locations, nearest neighbour (NN) classification algorithm is performed.
+Exemplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect.
 The method is evaluated in three different datasets of different lighting conditions.
-Additional depth information beside the actual image increases the detection rate especially in dark.
-The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known Simultaneously Localization and mapping (SLAM) problem.
-This technique is quite simple because of its low computational complexity, and performs in real-time with high loop closing accuracy.
+Additional depth information with the actual image increases the detection rate especially in dark environments.
+The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known simultaneously localization and mapping (SLAM) problem.
+This technique is also practically applicable because of its low computational complexity, and performing capability in real-time with high loop closing accuracy.
 
@@
 The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other.
-The tests are done with either using grayscale and depth images separately or using both of them.
+The tests are done with either using gray and depth images separately or using both of them.
 After that, the difference matrices are calculated to examine the results.
-Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
+The NN algorithm is applied to classify the new locations using the $L_{1}$ distance metric.
 In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.
@@
 
-The results are obtained by three datasets in which the trajectory of the Kinect mounted moving platform is similar to each Dataset that is created in different lightning conditions: Bright, Dim and Dark.
+The results are obtained by three datasets for which the trajectory is similar.
+Each dataset that is created in different lightning conditions: Bright, Dim and Dark.
 In the first loop, there are no loop closures to detect.
@@
 The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.
-In addition to this, the similarity matrices calculated from each dataset is shown in \ref{fig:dist_matrices}.
+In addition to this, the similarity matrices calculated from each dataset is shown in Figure \ref{fig:dist_matrices}.
 The black dots corresponds to the detected loop closures at $90\%$ precision.
@@
 There exist limited number of techniques that operate in real-time without parallelization.
-The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU.
-In this setting, the extraction of Quantized local Zernike moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
-The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with.
+The speed tests are done with a MacBook Pro 7.1 Intel Core 2 Duo 2.4 GHz CPU.
+In this setting, the extraction of quantized local Zernike moments of an image of size $256\times 192$ pixels takes approximately $10ms$.
+The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(n)$ that depends on the number of frames to compare with.
 In other words, the amount of time needed to performs this search increases throughout the trajectory.
@@
         \caption{Similarity matrices of the captured images in experimental results.
-Condensed gray shades point out to positive alikeness between scenes.
+Condensed gray shades denotes the positive alikeness between scenes.
 The black dots in lower triangle indicates detected loop closures at $90\%$ precision.}
@@
 In conclusion, this paper presents a novel image description technique that is used to achieve loop closure detection within a SLAM framework.
-The technique works quite rapidly and operates in real-time.
-Moreover, it results successful loop closing on different lightning conditions by using the depth information.
+The technique performs rapidly and operates in real-time.
+Moreover, loop closure is done successfully on all the lighting conditions with the help of the depth information used.
 
@@
 
-Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory, and Borda Technology for the indoor dataset retrieval.
+Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory, and Borda Technology for the help with indoor dataset retrieval.
 

### 2014-12-02 latex-spie/article.tex
almost finished

@@
 One of the widely used methods in visual place recognition problem is the Bag of Words\cite{1238663} method.
-Also, there are some studies that uses additional depth information\cite{kerl2013-IROS} in loop closure problems.More information related to visual loop closing approaches can be found on the relevant survey \cite{Williams09}.
+Also, there are some studies that uses additional depth information\cite{kerl2013-IROS} in loop closure problems.
+More information related to visual loop closing approaches can be found on the relevant survey \cite{Williams09}.
 
@@
 
-The technique we implement relies on discrete Complex Zernike Moments (CZMs) in 2-dimensional space.
+The technique we implement relies on discrete complex Zernike moments (CZMs) in 2-dimensional space.
 They are extracted using a set of complex polynomials which form a complete orthogonal radial basis functions defined on the unit disc.
@@
 Detecting loop closing events can be considered as a machine learning problem which number of classes expands continuously when a new unseen location comes.
-We utilized Nearest Neighbour (NN) algorithm to classify locations by which the distance metric is the regular $L_1$ a.k.a.
+We utilized nearest neighbour algorithm to classify locations by which the distance metric is the regular $L_1$ a.k.a.
 Manhattan distance that is one of the simplest distance metric available.
@@
 The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other.
-The tests are done with either using gray and depth images separately or using both of them.
+The tests are done with either using grayscale and depth images separately or using both of them.
 After that, the difference matrices are calculated to examine the results.
@@
         %%% BRIGHT PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
+        \begin{subfigure}[b]{0.43\textwidth}
         \centering
@@
         %%% DIM PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
+        \begin{subfigure}[b]{0.43\textwidth}
         \centering
@@
         %%% DARK PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
+        \begin{subfigure}[b]{0.43\textwidth}
         \centering
@@
         %%% ALL PR CURVE
-        \begin{subfigure}[b]{0.48\textwidth}
+        \begin{subfigure}[b]{0.43\textwidth}
         \centering
@@
 
-The results are obtained by three datasets for which the trajectory is similar.
-Each dataset that is created in different lightning conditions: Bright, Dim and Dark.
-In the first loop, there are no loop closures to detect.
+The results are obtained from three datasets for which the trajectory of the testing platform was the same. Each dataset is gathered in different lighting conditions: bright, dim and dark.
 To examine the performance of the method, precision-recall (PR) curves are plotted for each dataset.
-The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image sources that are only grayscale images, only depth images and both.
+The figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} consist of PR curves belonging to test runs in which only grayscale images are present, only depth-images are present or both grayscale and depth images are present.
+In Figure \ref{subfig:pr_all}, using the test run done with both grayscale and depth images, a comparison plot is shown, consisting of three PR curves belonging to bright, dim and dark datasets.
 The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.
-In addition to this, the similarity matrices calculated from each dataset is shown in Figure \ref{fig:dist_matrices}.
+In addition to this, the similarity matrices calculated from each dataset is shown in Figure\ref{fig:dist_matrices}.
 The black dots corresponds to the detected loop closures at $90\%$ precision.
-As it can be seen in the similarity matrices, the algorithm performs quite successful results to detect loop closure event.
-
-%VANGELden
-%the performance shown in Table/figure is  representative as the results are obtained with a %manually annotated ….
-%our demo video provides qualitative loop closure results which may be considered to be more representative for our method’s performance
+As it can be seen in the similarity matrices, the algorithm accomplishes to detect loop closure events.
 
@@
         %%% BRIGHT DISTANCE MATRIX
-        \begin{subfigure}[b]{0.27\textwidth}
+        \begin{subfigure}[b]{0.30\textwidth}
         \centering
@@
         %%% DIM DISTANCE MATRIX
-        \begin{subfigure}[b]{0.27\textwidth}
+        \begin{subfigure}[b]{0.30\textwidth}
         \centering
@@
         %%% DARK DISTANCE MATRIX
-        \begin{subfigure}[b]{0.27\textwidth}
+        \begin{subfigure}[b]{0.30\textwidth}
         \centering

### 2014-12-02 latex-spie/article.tex
Finished git pushgit push

@@
 \documentclass[]{spie}  % use for US letter paper
+%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
+%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
 \usepackage{comment}
-%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
-%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
 \usepackage[]{graphicx}
@@
 Loop closure estimations\cite{sariyanidi_spie13}  are cast by matching images.
-Most of image-to-image techniques that rely on salient image patches, use small, low-level features such as SURF\cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{sariyanidi_iv, HoNewmanCIRA2005, CumminsNewmanIJRR08}.
-One of the widely used methods in visual place recognition problem is the Bag of Words\cite{1238663} method.
+Most of image-to-image techniques that rely on salient image patches, use small, low-level features such as SURF\cite{Bay06surf:speeded} extracted from the whole image \cite{sariyanidi_iv, HoNewmanCIRA2005, CumminsNewmanIJRR08}.
+One of the widely used methods in visual place recognition problem is the Bag of Words\cite{Csurka04visualcategorization} method.
 Also, there are some studies that uses additional depth information\cite{kerl2013-IROS} in loop closure problems.

### 2014-12-11 latex-spie/article.tex
Video screen shots are added

@@
 Each row of this matrix is linearly combined by weighting each of them as a power of $2$.
-Hence a column vector $\mathbf{C}$ is obtained with integer values ranging between $0$ and $2^{2K(n)-1}-1$:
+Hence a column vector $\mathbf{C}$ is obtained with integer values ranging between $0$ and $2^{2K(n)}-1$:
 
@@
 
-Finally, the histogram is defined that consists of $2^{2K(n)-1}$ bins, and each bin is filled with the number of occurrences of the integers in $\mathbf{C}$.
-Therefore, the input image $I_{p\times q}$ is described with a histogram of length of $2^{2K(n)-1}$.
+Finally, the histogram is defined that consists of $2^{2K(n)}$ bins, and each bin is filled with the number of occurrences of the integers in $\mathbf{C}$.
+Therefore, the input image $I_{p\times q}$ is described with a histogram of length of $2^{2K(n)}$.
 
@@
         \hspace{-3mm}
-        \caption{The precision-recall curves of our method.}
+        \caption{The precision-recall curves of the method.}
         \label{fig:pr_curves}
@@
 To examine the performance of the method, precision-recall (PR) curves are plotted for each dataset.
-The figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} consist of PR curves belonging to test runs in which only grayscale images are present, only depth-images are present or both grayscale and depth images are present.
+The Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} consist of PR curves belonging to test runs in which only grayscale images are present, only depth-images are present or both grayscale and depth images are present.
 In Figure \ref{subfig:pr_all}, using the test run done with both grayscale and depth images, a comparison plot is shown, consisting of three PR curves belonging to bright, dim and dark datasets.
 The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.
-In addition to this, the similarity matrices calculated from each dataset is shown in Figure\ref{fig:dist_matrices}.
+In addition to this, the similarity matrices calculated from each dataset is shown in Figure \ref{fig:dist_matrices}.
 The black dots corresponds to the detected loop closures at $90\%$ precision.
 As it can be seen in the similarity matrices, the algorithm accomplishes to detect loop closure events.
+In addition to this, the real-time performance of the method can be observed in the videos which screen shots are shown in Figures \ref{subfig:video_bright}, \ref{subfig:video_dim} and \ref{subfig:video_dark}.
 
@@
 
+% VIDEO SCREEN SHOTS
+\begin{figure}
+        \centering
+
+        % http://dx.doi.org/doi.number.goes.here
+        % \footnote{http://dx.doi.org/doi.number.goes.here}
+
+        %%% BRIGHT
+        \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/video_bright.png}    
+        \caption{Video 1: Bright\vspace{1mm}\\\scriptsize{http://dx.doi.org/doi.number.goes.here}}
+        %%% ATTENTION !!! 
+        %%% IF THE LINKS ARE OVERLAPPED, USE \scriptsize INSTEAD OF \footnotesize
+        \label{subfig:video_bright}
+        \end{subfigure}
+        ~ 
+        %%% DIM 
+        \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/video_dim.png}    
+        \caption{Video 2: Dim\vspace{1mm}\\\scriptsize{http://dx.doi.org/doi.number.goes.here}}
+        \label{subfig:video_dim}
+        \end{subfigure}
+         ~ 
+        %%% DARK 
+        \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+         % trim parameters by order: left, bottom, right, top
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{figures/video_dark.png}    
+        \caption{Video 3: Dark\vspace{1mm}\\\scriptsize{http://dx.doi.org/doi.number.goes.here}}
+        \label{subfig:video_dark}
+        \end{subfigure}
+
+        \hspace{-2mm}
+        \caption{Exemplar video screen shots of the video showing the real-time performance of the method.
+The images on the left side indicates the current grayscale and depth images with their frame index.
+On the right side, images correspond to previously visited location are screened.
+True positives (TP), false positives (FP), false negatives (FN) and true negatives (TN) counted from the beginning are reported under the images.
+Also, the number of loop closures and processing time of the current frame are shown at the bottom.}
+        \label{fig:videos}
+\end{figure}
+
 %----------------------------------------------------------------------------------------------------
